---
title: "Thesis Cleaning"
author: "Nate Bender"
date: "12/3/2021"
note: "Nationally-representative survey; conducted Aug 3-9, 2020"
output: html_document
---

```{r child code and missing values extra ignore, eval=F, include=F, echo=F}
# COMMENTING OUT THIS BLOCK OF CODE FOR NOW. CAN COME BACK TO IT LATER IF WE WANT TO GET MORE GRANULAR WITH SEPARATING CHILDREN>18 AND DEPENDENTS. 
# # children_responded dummy var (1 category: 1==q answered, NA==question skipped)
# d_accept <- d_accept %>%
#   mutate(children_responded = ifelse(d_accept$sr_57i_dependents >= 1 | d_accept$sr_57j_adultchildren >= 1 | d_accept$sr_57k_nochildren==0,1,0))
# 
# # Dummy var for children under 18 / 273 w dependents
# d_accept <- d_accept %>%
#   mutate(dependents_dumvar = ifelse(children_responded==1 & sr_57i_dependents >=1,1,0))
# describe(d_accept$dependents_dumvar==1)
# 
# # Dummy var for adult children / 391 w adult children
# d_accept <- d_accept %>%
#   mutate(adultchild_dumvar = ifelse(children_responded==1 & sr_57j_adultchildren >=1,1,0))
# describe(d_accept$adultchild_dumvar==1)
# 
# # Dummy var for no children / 109 w/o children
# d_accept <- d_accept %>% 
#   mutate(nochildren_dumvar = ifelse(children_responded==1 & adultchild_dumvar==0 & dependents_dumvar==0,1,0))
# describe(d_accept$nochildren_dumvar==1)
# 
# # 62 respondents who have both dependents and adult children
# d_accept %>% 
#   mutate(test = ifelse(d_accept$sr_57j_adultchildren>=1 & d_accept$sr_57i_dependents>=1,1,0)) %>% 
#   count(test)
 

#
#
#


### Checking missing values
# # Checking for missing values across all variables. 
# # Pulled this code randomly from internet. No idea how it works. 
# 
# cbind(
#    lapply(
#      lapply(d_accept, is.na)
#      , sum)
#    )
# 
# # ton of missing data on these questions:
# # 40[a-r] 
# # 14[a-j]
# # 43-46


# # Percentages of missing data by variable
# missingpercentages <- function(x) {sum(is.na(x))/length(x)*100}
# apply(d_accept, 2, missingpercentages)

# # Check missing values for only variables used in OLR, NOT INCLUDING THE VARS USED IN THE FACTOR ANALYSIS
# OLRorigvarsmissing <- d_accept %>% dplyr::select(
#   matches("sr_12a_actions_contacted_officials"),
#   matches("gender"),
#   matches("age"),
#   -matches("age_range"),
#   matches("race_present_dumvar"),
#   matches("children_responded"),
#   matches("sr_19a_contacting_officials__parents"),
#   matches("sr_20a_rolemodels_parents"),
#   matches("sr_22a_expect_contact_parents"),
#   matches("sr_7_believe_about_climate_change"),
#   matches("sr_11_harm_future_generations"),
#   matches("sr_21a_effective_actions_contacting_officials"),
#   matches("sr_30_easy_to_call"),
#   matches("sr_31_able_to_call"),
#   matches("sr_41a_right_to_modify"),
#   matches("sr_41b_laws_of_nature"),
#   matches("sr_41c_ingenuity"),
#   matches("sr_41d_impotent"),
#   matches("sr_41e_govt_do_more"),
#   matches("sr_41f_equity"),
#   matches("sr_56_marital_status"),
#   matches("sr_61_education"),
#   matches("sr_71_employment_status"),
#   matches("sr_72_income"),
#   matches("sr_75b_religious"),
#   matches("sr_78_political_affiliation"),
#   matches("sr_79_political_leaning")
# )
# p_missing <- unlist(lapply(OLRorigvarsmissing, function(x) sum(is.na(x))))/nrow(d_accept)
# sort(p_missing[p_missing > 0], decreasing = TRUE)


# # Checking missing values in all original vars that went into factor analysis and subsequently into composite variables.
# 
# OLRcompvarsmissing <- d_accept %>% dplyr::select(
#   matches("sr_24_past_contact"),
#   matches("sr_25_future_contact"),
#   
#   matches("sr_19b_contacting_officials_spouse"),
#   matches("sr_19c_contacting_officials_children"),
# 
#   matches("sr_19d_contacting_officials_otherfamily"),
#   matches("sr_19e_contacting_officials_friends"),
#   matches("sr_19f_contacting_officials_coworkers"),
#   matches("sr_19g_contacting_officials_recpartners"),
#   matches("sr_19h_contacting_officials_faithcommun"),
# 
#   matches("sr_20b_rolemodels_spouse"),
#   matches("sr_20c_rolemodels_children"),
# 
#   matches("sr_20d_rolemodels_otherfamily"),
#   matches("sr_20e_rolemodels_friends"),
#   matches("sr_20f_rolemodels_coworkers"),
#   matches("sr_20g_rolemodels_recpartners"),
#   matches("sr_20h_rolemodels_faithcommun"),
# 
#   matches("sr_22b_expect_contact_spouse"),
#   matches("sr_22c_expect_contact_children"),
# 
#   matches("sr_22d_expect_contact_otherfamily"),
#   matches("sr_22e_expect_contact_friends"),
#   matches("sr_22f_expect_contact_coworkers"),
#   matches("sr_22g_expect_contact_recpartners"),
#   matches("sr_22h_expect_contact_faithcommun"),
# 
#   matches("sr_23a_motivated_to_comply_parents"),
#   matches("sr_23b_motivated_to_comply_spouse"),
#   matches("sr_23c_motivated_to_comply_children"),
# 
#   matches("sr_23d_motivated_to_comply_otherfamily"),
#   matches("sr_23e_motivated_to_comply_friends"),
#   matches("sr_23f_motivated_to_comply_coworkers"),
#   matches("sr_23g_motivated_to_comply_recpartners"),
#   matches("sr_23h_motivated_to_comply_faithcommun"),
# 
#   matches("sr_16_hear_friends_talk"),
#   matches("sr_17_hear_media"),
#   matches("sr_18_hear_public_officials"),
# 
#   matches("sr_3b_importance_climatechange"),
#   matches("sr_8_importance_personally"),
#   matches("sr_9_worried"),
#   matches("sr_10_harm_you_personally"),
# 
#   matches("sr_29a_effective_fed"),
#   matches("sr_29b_effective_state"),
#   matches("sr_29c_effective_business"),
#   matches("sr_29d_effective_ngo"),
# 
#   matches("sr_27a_competent_fed"),
#   matches("sr_27b_competent_state"),
#   matches("sr_27c_competent_business"),
#   matches("sr_28a_responsive_fed"),
#   matches("sr_28b_responsive_state"),
#   matches("sr_28c_responsive_business"),
# 
#   matches("sr_27d_competent_ngo"),
#   matches("sr_28d_responsive_ngo"),
# 
#   matches("sr_38_contact_admirable"),
#   matches("sr_39_contact_good"),
# 
#   matches("sr_32_contact_useful"),
#   matches("sr_33_contact_pleasant"),
#   matches("sr_37_contact_foolish"),
# 
#   matches("sr_34_contact_cool"),
#   matches("sr_35_contact_easy"),
#   matches("sr_36_contact_exciting"))
# p_missing <- unlist(lapply(OLRcompvarsmissing, function(x) sum(is.na(x))))/nrow(d_accept)
# sort(p_missing[p_missing > 0], decreasing = TRUE)


```

```{r setup, include=F}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load packages and data, eval=T, echo=F, include=F}
### Packages / libraries / load data & filter rejected out 

setwd("/Users/natebender/Desktop/repo/RCthesisanalysis/")

library(DescTools)
library(broom)
library(brant)
library(tidyr)
library(lmtest)  #lrtest
library(nortest)  #sf.test
library(ResourceSelection)  #hoslem.test
library(nnet)

library(psych)
library(tidyverse)
library(ggplot2)
library(GGally)
library(ggfortify)
library(ggcorrplot)
library(ggpubr)

library(GPArotation)
library(ltm)
library(fBasics)
library(car)
library(fastDummies)
library(MASS)
library(Hmisc)
library(dplyr)


# Load data, create second dataset of only accepted responses
d <- read.csv("/Users/natebender/Desktop/repo/RCthesisanalysis/dyn_national_20200828 - results-20200930-082116_NEW.csv")

d_accept <- d %>% 
  dplyr::filter(reject == 0)

```

## Outline
This document serves two functions: as Nate's detailed reference for steps and assumptions taken during analysis, and more broadly to communicate the analysis findings to advisors. Feel free to skip granular sections as needed.   

The analysis seeks to answer my thesis research questions:  
  
RQ1: Which explanatory variables from a variety of studies and theories are most strongly associated with climate activism, specifically the action of contacting elected officials?   
  
RQ2: How might we define behaviorally oriented segments and which segments are specifically related to the climate change activism behavior “contacting elected officials”?

At this point, the code only extends to RQ1. 

Table of contents:  
1) Variable renaming & cleanup  
2) Factor analysis & composite variables creation  
3) EDA & description of categorical variables levels reduction  
4) Listwise deletion & description of final dataset for analysis
5) Regression modelling approaches


## Variable renaming, cleanup, listwise deletion
```{r, eval=T, echo=F, include=T}
# rename 19a parents var b/c it's misspelled
d_accept <- dplyr::rename(d_accept, sr_19a_contacting_officials_parents = sr_19a_contacting_officials__parents)

# rename 37_foolish to _sensible to align with other wordings in this group (q32-39).
d_accept <- rename(d_accept, sr_37_contact_sensible = sr_37_contact_foolish)

# Change the obviously erroneous value of 99 dependents to NA
d_accept <- d_accept %>% 
    mutate(sr_57i_dependents = na_if(sr_57i_dependents, 99))  

# Create new variable w/ correct age calculated
d_accept <- d_accept %>% 
  mutate(age_true = 2020-year_born)

# Remove everyone under 18 years of age
d_accept <- subset(d_accept, age_true>=18)

# Convert RV (12a) past contact to an ordered factor and assign labels
d_accept$sr_12a_actions_contacted_officials <- recode_factor(d_accept$sr_12a_actions_contacted_officials, "1"="nocontact", "2"="once", "3"="morethanonce")
d_accept$sr_12a_actions_contacted_officials <- ordered(d_accept$sr_12a_actions_contacted_officials)

# Reverse code several variables so that the answer options make sense quantitatively and are consistent with rest of survey structure
# 3, 8, 9, 10, 11, 24, 25, 26
d_accept <- d_accept %>% 
  mutate(sr_3b_importance_climatechange_reversed = car::recode(sr_3b_importance_climatechange, "1=5 ; 2=4 ; 3=3 ; 4=2 ; 5=1"),
         sr_8_importance_personally_reversed = car::recode(sr_8_importance_personally, "1=5 ; 2=4 ; 3=3 ; 4=2 ; 5=1"),
         sr_9_worried_reversed = car::recode(sr_9_worried, "1=4 ; 2=3 ; 3=2 ; 4=1"),
         sr_10_harm_you_personally_reversed = car::recode(sr_10_harm_you_personally, "1=4 ; 2=3 ; 3=2 ; 4=1"),
         sr_11_harm_future_generations_reversed = car::recode(sr_11_harm_future_generations, "1=4 ; 2=3 ; 3=2 ; 4=1"),
         sr_24_past_contact_reversed = car::recode(sr_24_past_contact, "1=5 ; 2=4 ; 3=3 ; 4=2 ; 5=1"),
         sr_25_future_contact_reversed = car::recode(sr_25_future_contact, "1=5 ; 2=4 ; 3=3 ; 4=2 ; 5=1"),
         sr_26_identity_reversed = car::recode(sr_26_identity, "1=5 ; 2=4 ; 3=3 ; 4=2 ; 5=1"))

# Change all "don't know" or "don't know / does not apply" answers to NA
d_accept <- d_accept %>% 
  dplyr::mutate(  # check out "across()"
    sr_10_harm_you_personally_reversed = na_if(sr_10_harm_you_personally_reversed, 5),
    sr_11_harm_future_generations_reversed = na_if(sr_11_harm_future_generations_reversed, 5),
    sr_19a_contacting_officials_parents = na_if(sr_19a_contacting_officials_parents, 5),
    sr_19b_contacting_officials_spouse = na_if(sr_19b_contacting_officials_spouse, 5),
    sr_19c_contacting_officials_children = na_if(sr_19c_contacting_officials_children, 5),
    sr_19d_contacting_officials_otherfamily = na_if(sr_19d_contacting_officials_otherfamily, 5),
    sr_19e_contacting_officials_friends = na_if(sr_19e_contacting_officials_friends, 5),
    sr_19f_contacting_officials_coworkers = na_if(sr_19f_contacting_officials_coworkers, 5),
    sr_19g_contacting_officials_recpartners = na_if(sr_19g_contacting_officials_recpartners, 5),
    sr_19h_contacting_officials_faithcommun = na_if(sr_19h_contacting_officials_faithcommun, 5),
    sr_20a_rolemodels_parents = na_if(sr_20a_rolemodels_parents, 5),
    sr_20b_rolemodels_spouse = na_if(sr_20b_rolemodels_spouse, 5),
    sr_20c_rolemodels_children = na_if(sr_20c_rolemodels_children, 5),
    sr_20d_rolemodels_otherfamily = na_if(sr_20d_rolemodels_otherfamily, 5),
    sr_20e_rolemodels_friends = na_if(sr_20e_rolemodels_friends, 5),
    sr_20f_rolemodels_coworkers = na_if(sr_20f_rolemodels_coworkers, 5),
    sr_20g_rolemodels_recpartners = na_if(sr_20g_rolemodels_recpartners, 5),
    sr_20h_rolemodels_faithcommun = na_if(sr_20h_rolemodels_faithcommun, 5),
    sr_22a_expect_contact_parents = na_if(sr_22a_expect_contact_parents, 5),
    sr_22b_expect_contact_spouse = na_if(sr_22b_expect_contact_spouse, 5),
    sr_22c_expect_contact_children = na_if(sr_22c_expect_contact_children, 5),
    sr_22d_expect_contact_otherfamily = na_if(sr_22d_expect_contact_otherfamily, 5),
    sr_22e_expect_contact_friends = na_if(sr_22e_expect_contact_friends, 5),
    sr_22f_expect_contact_coworkers = na_if(sr_22f_expect_contact_coworkers, 5),
    sr_22g_expect_contact_recpartners = na_if(sr_22g_expect_contact_recpartners, 5),
    sr_22h_expect_contact_faithcommun = na_if(sr_22h_expect_contact_faithcommun, 5),
    sr_23a_motivated_to_comply_parents = na_if(sr_23a_motivated_to_comply_parents, 5),
    sr_23b_motivated_to_comply_spouse = na_if(sr_23b_motivated_to_comply_spouse, 5),
    sr_23c_motivated_to_comply_children = na_if(sr_23c_motivated_to_comply_children, 5),
    sr_23d_motivated_to_comply_otherfamily = na_if(sr_23d_motivated_to_comply_otherfamily, 5),
    sr_23e_motivated_to_comply_friends = na_if(sr_23e_motivated_to_comply_friends, 5),
    sr_23f_motivated_to_comply_coworkers = na_if(sr_23f_motivated_to_comply_coworkers, 5),
    sr_23g_motivated_to_comply_recpartners = na_if(sr_23g_motivated_to_comply_recpartners, 5),
    sr_23h_motivated_to_comply_faithcommun = na_if(sr_23h_motivated_to_comply_faithcommun, 5))

```

```{r new variables, eval=T, echo=F, include=F}
# Creating new variables where needed

# RACE
# Create race_present variable. Gives a "1" if race of any kind was entered, and an NA if not. 
d_accept <- d_accept %>%
  mutate(race_present_dumvar = ifelse(sr_74_1_race_white==1 | sr_74_2_race_black==2 | sr_74_3_race_hispanic==3 | sr_74_4_race_native_american==4 | sr_74_5_race_east_asian==5 | sr_74_6_race_middle_eastern==6 | sr_74_7_race_south_asian==7,1,0))
# Gives us 1 where race_white==1, and NA if otherwise
d_accept <- d_accept %>% 
  mutate(race_white_dumvar = ifelse(sr_74_1_race_white==1,1,NA))         
# Replace all instances of NA with zero. This will now grab all instances of "race_other" with zero, but also rows where race isn't present. 
d_accept$race_white_dumvar[is.na(d_accept$race_white_dumvar)] <-0
# Lastly filter out rows where respondent truly skipped the question. For column "race_white_dumvar", replace any value (will be 0 or 1) with NA for any row where "race_present_dumvar" is NA. Which leaves us with 1=="white" and 0=="other"
d_accept$race_white_dumvar[is.na(d_accept$race_present_dumvar)] <- d_accept$race_present_dumvar[is.na(d_accept$race_present_dumvar)] 
d_accept$race_white_dumvar <- recode_factor(d_accept$race_white_dumvar, "1"="race_white", "0"="race_other")

# GENDER
# Turn Gender variable into only two factors: male and female. "Other" and "prefer not to answer" get turned into NA and dropped. 
d_accept <- d_accept %>%
  mutate(gender_dumvar = factor(d_accept$gender, ordered=FALSE))
d_accept$gender_dumvar <- recode_factor(d_accept$gender, "1"="female", "2"="male")
levels(d_accept$gender_dumvar)[levels(d_accept$gender_dumvar)=="3"] <- NA
levels(d_accept$gender_dumvar)[levels(d_accept$gender_dumvar)=="4"] <- NA

# CHILDREN
# Dummy var for any respondent w children of any age
d_accept <- d_accept %>% 
  mutate(children_dumvar = ifelse(d_accept$sr_57j_adultchildren>=1 | d_accept$sr_57i_dependents>=1,1,0))
d_accept$children_dumvar <- recode_factor(d_accept$children_dumvar, "1"="children", "0"="nochildren")

# RELIGION
# Original levels:
# d_accept$sr_75_religion <- recode_factor(d_accept$sr_75_religion, "1"="catholic", "2"="main_protestant", "3"="evangelical", "4"="oth_christian", "5"="mormon", "6"="unitarian", "7"="jewish", "8"="muslim", "9"="hindu", "10"="buddhist", "11"="oth_nonchristian", "12"="spiritual", "13"="atheist", "14"="agnostic", "0"="other")
d_accept <- d_accept %>% 
  mutate(sr_75_religion_dumvar = factor(d_accept$sr_75_religion, ordered=FALSE))
d_accept$sr_75_religion_dumvar <- recode_factor(d_accept$sr_75_religion, "1"="religious", "2"="religious", "3"="religious", "4"="religious", "5"="religious", "6"="religious", "7"="religious", "8"="religious", "9"="religious", "10"="religious", "11"="religious", "12"="notreligious", "13"="notreligious", "14"="notreligious", "0"="notreligious")

```

## Factor Analysis
$$\\[.05in]$$
### Dynamic Norms
*"Do you think that over the PAST/NEXT 12 months the percentage of adults in the United States who contacted elected officials to urge them to take action to reduce global warming is..."*   

One factor solution:   
1. Two-item factor consisting of the two dynamic norms questions (changes in the number of ppl contacting reps in the past and future)
```{r, eval=T, echo=F, warning=F}
res <- cor.test(d_accept$sr_24_past_contact_reversed,d_accept$sr_25_future_contact_reversed, method = "spearman")
print(res)

# Create composite variable
d_accept <- d_accept %>% 
  mutate(
    descdynamicnorms_comp = rowMeans(subset(d_accept[, c("sr_24_past_contact", "sr_25_future_contact")], na.rm=T)))

# test <- d_accept %>% 
 # dplyr::select(descdynamicnorms_comp, sr_24_past_contact, sr_25_future_contact)
```
Correlation test of the two dynamic norms items shows moderate positive correlation, with Spearman's rho of `r res$estimate` and p-value of `r res$p.value`.

$$\\[.05in]$$

### Descriptive Norms
(contact) *"To what extent do you think that the following people ARE CONTACTING (writing letters, emailing, or calling) their elected representatives in Congress to urge action on reducing climate change?"*
  
(role models) *"How likely are you to consider each of these groups as behavioral role models?"*  
  
Two factor solution (73% cumulative variance (hereafter: cv))   
1. All "contact" items
2. All "role model" items

```{r, eval=T, echo=F}
d_pca_descriptivenorms <- d_accept %>% 
  dplyr::select(
  matches("sr_19a_contacting_officials_parents"),
  matches("sr_19b_contacting_officials_spouse"),
  matches("sr_19c_contacting_officials_children"),
  matches("sr_19d_contacting_officials_otherfamily"),
  matches("sr_19e_contacting_officials_friends"),
  matches("sr_19f_contacting_officials_coworkers"),
  matches("sr_19g_contacting_officials_recpartners"),
  matches("sr_19h_contacting_officials_faithcommun"),
  matches("sr_20a"),
  matches("sr_20b"),
  matches("sr_20c"),
  matches("sr_20d"),
  matches("sr_20e"),
  matches("sr_20f"),
  matches("sr_20g"),
  matches("sr_20h"))
  
fa.parallel(d_pca_descriptivenorms, fm='minres', fa='fa')
pca1 <- fa(d_pca_descriptivenorms, nfactors = 2, rotate = "Varimax", fm="minres") 
print(pca1)
print(pca1$loadings,cutoff = 0.3)

```

#### Descriptive Norms (contact) - 1st factor (all) - Cronbach Alpha
```{r, eval=T, echo=F, include=F}
d_pca_descriptivecontactnorms_all <- d_accept %>% 
  dplyr::select(
    matches("sr_19a_contacting_officials_parents"),
    matches("sr_19b_contacting_officials_spouse"),
    matches("sr_19c_contacting_officials_children"),
    matches("sr_19d_contacting_officials_otherfamily"),
    matches("sr_19e_contacting_officials_friends"),
    matches("sr_19f_contacting_officials_coworkers"),
    matches("sr_19g_contacting_officials_recpartners"),
    matches("sr_19h_contacting_officials_faithcommun"))

psych::alpha(d_pca_descriptivecontactnorms_all, use ="pairwise") 
```
.97 alpha indicates strong reliability. Decreases if any are dropped. 

```{r, eval=T, echo=T, include=F}
# Create  new comp variable
d_accept <- d_accept %>% 
  mutate(
    desccontactnorms_all_comp = rowMeans(d_accept[, c("sr_19a_contacting_officials_parents", "sr_19b_contacting_officials_spouse", "sr_19c_contacting_officials_children", "sr_19d_contacting_officials_otherfamily", "sr_19e_contacting_officials_friends", "sr_19f_contacting_officials_coworkers", "sr_19g_contacting_officials_recpartners", "sr_19h_contacting_officials_faithcommun")], na.rm=T))
    
# Check to see if the code works correctly
# test <- d_accept %>% 
#   dplyr::select(desccontactnorms_all_comp, sr_19a_contacting_officials_parents, sr_19b_contacting_officials_spouse, sr_19c_contacting_officials_children, sr_19d_contacting_officials_otherfamily, sr_19e_contacting_officials_friends, sr_19f_contacting_officials_coworkers, sr_19g_contacting_officials_recpartners, sr_19h_contacting_officials_faithcommun)
    
```

$$\\[.05in]$$
#### Descriptive Norms (role models) - 2nd factor (All) - Cronbach Alpha
```{r, eval=T, echo=F}
d_pca_descriptiverolemodelnorms_all <- d_accept %>% 
  dplyr::select(
    matches("sr_20a_rolemodels_parents"),
    matches("sr_20b_rolemodels_spouse"),
    matches("sr_20c_rolemodels_children"),
    matches("sr_20d_rolemodels_otherfamily"),
    matches("sr_20e_rolemodels_friends"),
    matches("sr_20f_rolemodels_coworkers"),
    matches("sr_20g_rolemodels_recpartners"),
    matches("sr_20h_rolemodels_faithcommun"))

psych::alpha(d_pca_descriptivecontactnorms_all, use ="pairwise") 
```
Alpha of .94 shows strong reliability, with no significant improvement found by dropping any items. 

```{r, eval=T, echo=F, include=F}
# Create two comp variables
d_accept <- d_accept %>% 
  mutate(
    descrolemodelnorms_all_comp = rowMeans(d_accept[, c("sr_20a_rolemodels_parents", "sr_20b_rolemodels_spouse", "sr_20c_rolemodels_children", "sr_20d_rolemodels_otherfamily", "sr_20e_rolemodels_friends", "sr_20f_rolemodels_coworkers", "sr_20g_rolemodels_recpartners", "sr_20h_rolemodels_faithcommun")], na.rm=T))
```

$$\\[.05in]$$
### Injunctive Norms 
(contact) *"To what extent do you think that the following people EXPECT YOU to contact (writing letters, emailing, or calling) your elected representatives to urge action on reducing climate change?"*

(motivation) *"How motivated are you to comply with the expectations of each of these people?"*
  
Scree plot suggests two factors (76% cv).
1. All "contact" items
2. All "motivation" items

```{r, eval=T, echo=F}
d_pca_injunctivecontactnorms <- d_accept %>% 
  dplyr::select(
    matches("sr_22a"),
    matches("sr_22b"),
    matches("sr_22c"),
    matches("sr_22d"),
    matches("sr_22e"),
    matches("sr_22f"),
    matches("sr_22g"),
    matches("sr_22h"),
    matches("sr_23a"),
    matches("sr_23b"),
    matches("sr_23c"),
    matches("sr_23d"),
    matches("sr_23e"),
    matches("sr_23f"),
    matches("sr_23g"),
    matches("sr_23h"))

fa.parallel(d_pca_injunctivecontactnorms, fm='minres', fa='fa')
pca1 <- fa(d_pca_injunctivecontactnorms, nfactors = 2, rotate = "Varimax", fm="minres") 
print(pca1)
print(pca1$loadings,cutoff = 0.3)

# # 4
# fa.parallel(d_pca_injunctivecontactnorms, fm='minres', fa='fa')
# pca1 <- fa(d_pca_injunctivecontactnorms, nfactors = 4, rotate = "Varimax", fm="minres") 
# print(pca1)
# print(pca1$loadings,cutoff = 0.3)
```
#### Injunctive Norms (contact) - 1st factor (All) - Cronbach Alpha
```{r, eval=T, echo=F}
d_pca_injunctivenorms_all <- d_accept %>% 
  dplyr::select(
    matches("sr_22a"),
    matches("sr_22b"),
    matches("sr_22c"),
    matches("sr_22d"),
    matches("sr_22e"),
    matches("sr_22f"),
    matches("sr_22g"),
    matches("sr_22h"))

psych::alpha(d_pca_injunctivenorms_all, use ="pairwise") 
```
.98 alpha shows high reliability. Dropping any items decreases the alpha. 

```{r, eval=T, echo=F, include=F}
# Create two comp variables
d_accept <- d_accept %>% 
  mutate(
    injunctcontactnorms_all_comp = rowMeans(d_accept[, c("sr_22a_expect_contact_parents", "sr_22b_expect_contact_spouse", "sr_22c_expect_contact_children", "sr_22d_expect_contact_otherfamily", "sr_22e_expect_contact_friends", "sr_22f_expect_contact_coworkers", "sr_22g_expect_contact_recpartners", "sr_22h_expect_contact_faithcommun")], na.rm=T))
```
$$\\[.05in]$$

#### Injunctive Norms (motivation) - 2nd factor (all) - Cronbach Alpha
```{r, eval=T, echo=F}
d_pca_injunctivemotivation_all <- d_accept %>% 
  dplyr::select(
    matches("sr_23a_motivated_to_comply_parents"),
    matches("sr_23b_motivated_to_comply_spouse"),
    matches("sr_23c_motivated_to_comply_children"),
    matches("sr_23d_motivated_to_comply_otherfamily"),
    matches("sr_23e_motivated_to_comply_friends"),
    matches("sr_23f_motivated_to_comply_coworkers"),
    matches("sr_23g_motivated_to_comply_recpartners"),
    matches("sr_23h_motivated_to_comply_faithcommun"))

psych::alpha(d_pca_injunctivemotivation_all, use ="pairwise") 
```
.94 alpha shows strong reliabiity; no increase with dropping any items.  

```{r, eval=T, echo=F, include=F}
# Create two comp variables
d_accept <- d_accept %>% 
  mutate(
    injunctmotivation_all_comp = rowMeans(d_accept[, c("sr_23a_motivated_to_comply_parents", "sr_23b_motivated_to_comply_spouse",  "sr_23c_motivated_to_comply_children", "sr_23d_motivated_to_comply_otherfamily", "sr_23e_motivated_to_comply_friends", "sr_23f_motivated_to_comply_coworkers", "sr_23g_motivated_to_comply_recpartners", "sr_23h_motivated_to_comply_faithcommun")], na.rm=T))
```

$$\\[.05in]$$
### CIM - Benefits
*"How often do you hear ____ talk about the importance of reducing climate change?"*   
*[your friends, family, and coworkers]*   
*[public figures whom you respect]*   
*[about the importance of reducing climate change in the media? (TV, movies, radio, newspapers/news websites, magazines, etc.)]*

One-factor solution (58% cv):   
1. Multi-item composite variable: F/Fam/Cowork, Public Figures, Media

```{r, eval=T, echo=F}
d_pca_CIMbenefits <- d_accept %>% 
  dplyr::select(
    matches("sr_16"),
    matches("sr_17"),
    matches("sr_18"))

fa.parallel(d_pca_CIMbenefits, fm='minres', fa='fa')
pca1 <- fa(d_pca_CIMbenefits, nfactors = 1, rotate = "Varimax", fm="minres") 
print(pca1)
print(pca1$loadings,cutoff = 0.3)
```

#### CIM - Benefits - Cronbach Alpha
```{r, eval=T, echo=F}
psych::alpha(d_pca_CIMbenefits, use ="pairwise") 

# Create comp variable
d_accept <- d_accept %>% 
  mutate(
    cimbenefits_comp = rowMeans(d_accept[, c("sr_16_hear_friends_talk", "sr_17_hear_media", "sr_18_hear_public_officials")], na.rm=T))
```
.79 alpha indicates good reliability; no increase with dropping any of the three items. 

$$\\[.05in]$$
### CIM - Perceived Risk
*"How important is each of the following issues to you today?"*   
*"How important is the issue of climate change to you personally?"*   
*"How worried are you about climate change?"*   
*"How much do you think climate change will harm you personally?"*   
*"How much do you think climate change will harm future generations of people?"*


Two-factor solution   
1. Multi-item composite variable: CC importance as an issue, CC personal importance, CC worry, belief of personal harm from CC    
2. 1-item variable: belief of harm to future generations from CC

```{r, eval=T, echo=F}
d_pca_CIMperceivedrisk <- d_accept %>% 
  dplyr::select(
    matches("sr_3b_importance_climatechange_reversed"),
    matches("sr_8_importance_personally_reversed"),
    matches("sr_9_worried_reversed"),
    matches("sr_10_harm_you_personally_reversed"),
    matches("sr_11_harm_future_generations_reversed"))

fa.parallel(d_pca_CIMperceivedrisk, fm='minres', fa='fa')
pca1 <- fa(d_pca_CIMperceivedrisk, nfactors = 3, rotate = "Varimax", fm="minres") 
print(pca1)
print(pca1$loadings,cutoff = 0.3)
```

#### CIM - Perceived Risk - 1st factor (Personal) - Cronbach Alpha
```{r, eval=T, echo=F}
d_pca_CIMperceivedrisk_importance_worry <- d_accept %>% 
  dplyr::select(
    matches("sr_3b_importance_climatechange_reversed"),
    matches("sr_8_importance_personally_reversed"),
    matches("sr_9_worried_reversed"))

psych::alpha(d_pca_CIMperceivedrisk_importance_worry, use ="pairwise") 
```
.91 alpha shows strong reliability; decreases when any items are dropped. 

#### CIM - Perceived Risk - 2nd factor - correlation
```{r, eval=F, echo=F, include=F}
res <- cor.test(d_accept$sr_10_harm_you_personally_reversed,d_accept$sr_11_harm_future_generations_reversed, method = "spearman")
print(res)
```
The two measures of perceived risk show a slightly positive relationship. Spearman's rho is `r res$estimate` with a p-value of `r res$p.value`. Not a strong enough relationship to combine the variables; they will stay separate. 


```{r, eval=T, echo=F, include=T}
# Create single composite variable
d_accept <- d_accept %>% 
  mutate(
    cimperceivedrisk_comp = rowMeans(d_accept[, c("sr_3b_importance_climatechange_reversed", "sr_8_importance_personally_reversed", "sr_9_worried_reversed")], na.rm=T))

# single var
# sr_10_harm_you_personally_reversed

# single var
# describe(d_accept$sr_11_harm_future_generations_reversed)
```

$$\\[.05in]$$
### Efficacy
*"Below is a list of actions that individuals could take to reduce climate change. If YOU took these actions, how effective would each be for reducing climate change?"*   
*"Below are some public and private organizations who make decisions that have an impact on climate change. In general, how COMPETENT is each in addressing climate change?"*   
*"In general, how RESPONSIVE is each in addressing climate change?"*   
*"How much do you agree that each type of organization is generally IN A POSITION TO EFFECTIVELY reduce climate change?"* 

1. 1-item variable: 21a: Is contacting elected reps an effective action?  

Two-factor solution (61% cv):   
1. Multi-item composite variable: All types (fed, state, business, ngo) are in a position to effect change   
2. Multi-item composite variable: All types' (fed, state, business, ngo) competency and responsiveness   

```{r, eval=T, echo=F}
d_pca_efficacygroup <- d_accept %>% 
  dplyr::select(
    matches("sr_27[a-d]"),
    matches("sr_28[a-d]"),
    matches("sr_29[a-d]"))

fa.parallel(d_pca_efficacygroup, fm='minres', fa='fa')
pca1 <- fa(d_pca_efficacygroup, nfactors = 2, rotate = "Varimax", fm="minres") 
print(pca1)
print(pca1$loadings,cutoff = 0.3)
```

#### Efficacy - 1st variable (is contacting elected officials an effective action?)
```{r, eval=T, echo=F, include=F}
describe(d_accept$sr_21a_effective_actions_contacting_officials)
```

#### Efficacy - 1st Factor (All types' ability to effect change) - Cronbach Alpha 
```{r, eval=T, echo=F}
d_pca_efficacyeffectchange_all <- d_accept %>% 
  dplyr::select(
    matches("sr_29[a-d]"))

psych::alpha(d_pca_efficacyeffectchange_all, use ="pairwise") 
```
.93 alpha shows strong reliability, and it decreases when any items are dropped. 

#### Efficacy - 2nd Factor (all types' competency & responsiveness) - Cronbach Alpha 
```{r, eval=T, echo=F}
d_pca_efficacycompetencyresponsive_all <- d_accept %>% 
  dplyr::select(
    matches("sr_27[a-d]"),
    matches("sr_28[a-d]"))

psych::alpha(d_pca_efficacycompetencyresponsive_all, use ="pairwise") 
```
.88 alpha shows strong reliability, and it decreases when any items are dropped. 

```{r, eval=T, echo=F, include=F}
# Create two comp variables
d_accept <- d_accept %>% 
  mutate(
    efficacy_effectiveness_all_comp = rowMeans(d_accept[, c("sr_29a_effective_fed", "sr_29b_effective_state", "sr_29c_effective_business", "sr_29d_effective_ngo")], na.rm=T),
    efficacy_competresp_all_comp = rowMeans(d_accept[, c("sr_27a_competent_fed", "sr_27b_competent_state", "sr_27c_competent_business", "sr_27d_competent_ngo", "sr_28a_responsive_fed", "sr_28b_responsive_state", "sr_28c_responsive_business", "sr_28d_responsive_ngo")], na.rm=T))
```

$$\\[.05in]$$
### TPB Behavioral Attitude
*"For me, contacting (writing letters, emailing, phoning my elected representatives in Congress to urge action on climate change on a regular basis during the next year would be …"*

Three-factor solution:   
1. 2-item variable: admirable/shameful, good/bad   
2. Multi-item composite variable: useful/useless, pleasant/intimidating, sensible/foolish  
3. Multi-item composite variable: cool/uncool, easy/awkward, exciting/boring   
```{r, eval=T, echo=F}
# Reverse 34, 35, 36, 38, 39 so a higher number indicates something good, in line with the structure of the rest of the survey answers. 
# now 6=cool and 1=uncool
d_accept <- d_accept %>% 
  mutate(sr_34_contact_cool_reversed = car::recode(sr_34_contact_cool, "1=6 ; 2=5 ; 3=4 ; 4=3 ; 5=2 ; 6=1")) 
# now 6=easy and 1=awkward
d_accept <- d_accept %>% 
  mutate(sr_35_contact_easy_reversed = car::recode(sr_35_contact_easy, "1=6 ; 2=5 ; 3=4 ; 4=3 ; 5=2 ; 6=1"))
# now 6=exciting and 1=boring
d_accept <- d_accept %>%
  mutate(sr_36_contact_exciting_reversed = car::recode(sr_36_contact_exciting, "1=6 ; 2=5 ; 3=4 ; 4=3 ; 5=2 ; 6=1"))
# now 6=admirable and 1=shameful
d_accept <- d_accept %>%
  mutate(sr_38_contact_admirable_reversed = car::recode(sr_38_contact_admirable, "1=6 ; 2=5 ; 3=4 ; 4=3 ; 5=2 ; 6=1"))
# now 6=good and 1=bad
d_accept <- d_accept %>%
  mutate(sr_39_contact_good_reversed = car::recode(sr_39_contact_good, "1=6 ; 2=5 ; 3=4 ; 4=3 ; 5=2 ; 6=1"))

behattitude <- d_accept %>%
  dplyr::select(
    matches("sr_32_contact_useful"),
    matches("sr_33_contact_pleasant"),
    matches("sr_34_contact_cool_reversed"),
    matches("sr_35_contact_easy_reversed"),
    matches("sr_36_contact_exciting_reversed"),
    matches("sr_37_contact_sensible"),
    matches("sr_38_contact_admirable_reversed"),
    matches("sr_39_contact_good_reversed"))

fa.parallel(behattitude, fm='minres', fa='fa')
pca1 <- fa(behattitude, nfactors = 3, rotate = "Varimax", fm="minres") 
print(pca1)
print(pca1$loadings,cutoff = 0.3)

```

#### TPB Behavioral Attitude - 1st factor - Correlation
```{r, eval=T, echo=F}
res <- cor.test(d_accept$sr_38_contact_admirable_reversed,d_accept$sr_39_contact_good_reversed, method = "spearman")
print(res)
```
The two measures of perceived behavioral control ("admirable/shameful" and "good/bad") show a moderate positive relationship. Spearman's rho is `r res$estimate` with a p-value of `r res$p.value`.   

#### TPB Behavioral Attitude - 2nd factor - Cronbach Alpha
```{r, eval=T, echo=F}
d_pca_behavioralattitude2 <- d_accept %>% 
  dplyr::select(
    matches("sr_32_contact_useful"),
    matches("sr_33_contact_pleasant"),
    matches("sr_37_contact_sensible"))

psych::alpha(d_pca_behavioralattitude2, use ="pairwise") 
```
.80 alpha shows good reliability, and it decreases when any items are dropped. 

#### TPB Behavioral Attitude - 3rd factor - Cronbach Alpha
```{r, eval=T, echo=F}
d_pca_behavioralattitude3 <- d_accept %>% 
  dplyr::select(
    matches("sr_34_contact_cool_reversed"),
    matches("sr_35_contact_easy_reversed"),
    matches("sr_36_contact_exciting_reversed"))

psych::alpha(d_pca_behavioralattitude3, use ="pairwise") 
```
.77 alpha shows good reliability, and it decreases when any items are dropped. 

```{R, eval=T, echo=F, include=F}
# Create comp varialbes
d_accept <- d_accept %>% 
  mutate(
    behatt_admirablegood_comp = rowMeans(d_accept[, c("sr_38_contact_admirable_reversed", "sr_39_contact_good_reversed")], na.rm=T),
    behatt_usefulpleasantsensible_comp = rowMeans(d_accept[, c("sr_32_contact_useful", "sr_33_contact_pleasant", "sr_37_contact_sensible")], na.rm=T),
    behatt_coolexcitingeasy_comp = rowMeans(d_accept[, c("sr_34_contact_cool_reversed", "sr_35_contact_easy_reversed", "sr_36_contact_exciting_reversed")], na.rm=T))
```

$$\\[.05in]$$
### Perceived Behavioral Control - correlation  
*"Imagine the idea of calling an elected official on a regular basis over the next year."*    
*"30 - How easy would it be for you to make these calls on a regular basis?"*  
*"31 - How able might you be to make such calls on a regular basis?"*

```{r, eval=T, echo=F, warning=F}
res <- cor.test(d_accept$sr_30_easy_to_call,d_accept$sr_31_able_to_call, method = "spearman")
print(res)

#mean(OLR_complete_cases$sr_30_easy_to_call, na.rm=TRUE)
#sd(OLR_complete_cases$sr_30_easy_to_call, na.rm=TRUE)

#mean(OLR_complete_cases$sr_31_able_to_call, na.rm=TRUE)
#sd(OLR_complete_cases$sr_31_able_to_call, na.rm=TRUE)
```
The two measures of perceived behavioral control show a moderate-to-poor positive relationship, just barely under the .65 rule of thumb. Spearman's rho is `r res$estimate` with a p-value of `r res$p.value`. This is not a strong enough correlation to justify a composite variable of the two items, so they will stay separate.

$$\\[.05in]$$

### Worldviews
We decided these will be kept as-is.

```{r, eval=T, echo=F}
d_worldviews <- d_accept %>% 
  dplyr::select(
    matches("sr_41a"),
    matches("sr_41b"),
    matches("sr_41c"),
    matches("sr_41d"),
    matches("sr_41e"),
    matches("sr_41f"))

summary(d_worldviews)
sapply(d_worldviews, sd, na.rm=TRUE)
```
$$\\[.05in]$$

## Creating temp dataframe for desc stats on only the 506 responses for analysis, before combining categorical vars
```{r}
d_accept$sr_61_education <- factor(d_accept$sr_61_education, ordered=TRUE)

descstats_df <- d_accept %>% dplyr::select(
  matches("respondent_id"),
  matches("sr_12a_actions_contacted_officials"),
  matches("sr_13a_takeactions_contact_officials"),
  -matches("sr_12a_actions_contacted_officials_factor"),
  matches("descdynamicnorms_comp"),
  matches("desccontactnorms_all_comp"),
  matches("descrolemodelnorms_all_comp"),
  matches("injunctcontactnorms_all_comp"),
  matches("injunctmotivation_all_comp"),
  matches("cimbenefits_comp"),
  matches("cimperceivedrisk_comp"),
  matches("sr_10_harm_you_personally_reversed"),
  matches("sr_11_harm_future_generations_reversed"),
  matches("sr_21a_effective_actions_contacting_officials"),
  matches("efficacy_effectiveness_all_comp"),
  matches("efficacy_competresp_all_comp"),
  matches("behatt_admirablegood_comp"),
  matches("behatt_usefulpleasantsensible_comp"),
  matches("behatt_coolexcitingeasy_comp"),
  matches("sr_7_believe_about_climate_change"),
  matches("sr_30_easy_to_call"),
  matches("sr_31_able_to_call"),
  matches("sr_41a_right_to_modify"),
  matches("sr_41b_laws_of_nature"),
  matches("sr_41c_ingenuity"),
  matches("sr_41d_impotent"),
  matches("sr_41e_govt_do_more"),
  matches("sr_41f_equity"),
  matches("race_white_dumvar"),
  matches("children_dumvar"),
  matches("gender_dumvar"),
  matches("age_true"),
  -matches("age_range"),
  matches("sr_56_marital_status"),
  matches("sr_60_residence"),
  matches("sr_61_education"),
  matches("sr_71_employment_status"),
  matches("sr_72_income"),
  matches("sr_75_religion_dumvar"),
  matches("sr_78_political_affiliation"),
  matches("sr_79_political_leaning")
)
# listwise deletion
descstats_complete <- descstats_df[complete.cases(descstats_df), ]
dim(descstats_complete)[1] # responses
dim(descstats_complete)[2] # variables

describe(descstats_complete$sr_60_residence)
```


## EDA - Categorical variables factoring & levels reduction

#### EDA - Race
```{r eval=T, echo=F, include=T}
# RACE
# # Percentage of missing data on race - 21% missing
# totalvar <- count(respondents)
# 
# (totalvar - whitecount - othercount)/totalvar
# 
# # number of white respondents
# whitecount <- sum(d_accept$sr_74_1_race_white==1, na.rm = T)
# # number of other ethnicities
# othercount <- sum(d_accept$sr_74_2_race_black==2 | d_accept$sr_74_3_race_hispanic==3 | d_accept$sr_74_4_race_native_american==4 | d_accept$sr_74_5_race_east_asian==5 | d_accept$sr_74_6_race_middle_eastern==6 | d_accept$sr_74_7_race_south_asian==7, na.rm = T)


# levels(OLR_complete_cases$race_white_dumvar)
table_1 <- table(d_accept$sr_12a_actions_contacted_officials, d_accept$race_white_dumvar)
# total responses by religion type
table(d_accept$race_white_dumvar)

# proportion of total responses, grouped by religion option and level of response variable.
prop.table(table_1, margin=2)
```
Race variable reduced to two levels: "white" and "other". The question was a check-all-that-apply; if a respondent chose white along with any other races they were coded as white. 

1) Number of responses: `r table(d_accept$race_white_dumvar)[1]` white respondents and `r table(d_accept$race_white_dumvar)[2]` other respondents. 

2) Proportion of responses broken out by race

#### EDA - Q7 CC Belief
```{r eval=T, echo=F, include=T}
# CATEGORICAL VARIABLES re-coding
d_accept$sr_7_believe_about_climate_change <- factor(d_accept$sr_7_believe_about_climate_change, ordered=FALSE)
d_accept$sr_7_believe_about_climate_change <- recode_factor(d_accept$sr_7_believe_about_climate_change, "1"="notchanging", "2"="most_natural", "3"="natural_human", "4"="most_human", "5"="excl_human")
# total responses by religion type
table(d_accept$sr_7_believe_about_climate_change)
```
Number of responses by answer option. Leaving these categories as-is. 

#### EDA - Gender
```{r eval=T, echo=F, include=T}
# There are 1055 respondents in OLR_complete_cases, but I can only find a sum of 1049 respondents across all gender options and I can't find a way to display those skips/"n/a"s???
# d_accept %>% 
#   summarize(female = sum(gender==1, na.rm = TRUE),
#             femalepercent = sum(gender==1, na.rm = TRUE)/sum(gender, na.rm =TRUE),
#             male = sum(gender==2, na.rm = TRUE),
#             malepercent = sum(gender==2, na.rm = TRUE)/sum(gender, na.rm =TRUE),
#             other = sum(gender==3, na.rm = TRUE),
#             otherpercent = sum(gender==3, na.rm = TRUE)/sum(gender, na.rm =TRUE),
#             noanswer = sum(gender==4, na.rm = TRUE),
#             noanswerpercent = sum(gender==4, na.rm = TRUE)/sum(gender, na.rm =TRUE),
#             total = sum((gender==1)+(gender==2)+(gender==3)+(gender==4), na.rm = TRUE))


# levels(OLR_complete_cases$gender_dumvar)
table_1 <- table(d_accept$sr_12a_actions_contacted_officials, d_accept$gender_dumvar)
# total responses by religion type
table(d_accept$gender_dumvar)
# proportion of total responses, grouped by religion option and level of response variable.
prop.table(table_1, margin=2)
```
Total females and males, and response proportions by gender. 

#### EDA - Marital Status
Original levels:  
1="single" 2="married / partner" 3="divorced / separated" 4="widowed"
```{r eval=T, echo=F, include=T}
# MARITAL STATUS
d_accept$sr_56_marital_status <- factor(d_accept$sr_56_marital_status, ordered=FALSE)
#levels(OLR_complete_cases$sr_56_marital_status)
# Breakdown of responses
table(d_accept$sr_56_marital_status)
```
  
Collapsing down to three levels, though "Divorce/widow" might not have enough responses to support our analysis; need to double-check.
```{r eval=T, echo=F, include=T}
# Therefore, collapsing as follows:
# "single" and "married/partner" stay as-is
# "divorce" and "widow" -> "divorce_widow"
d_accept$sr_56_marital_status <- recode_factor(d_accept$sr_56_marital_status, "1"="single", "2"="married_partner", "3"="divorce_widow", "4"="divorce_widow")
# levels(OLR_complete_cases$sr_56_marital_status)
table_1 <- table(d_accept$sr_12a_actions_contacted_officials, d_accept$sr_56_marital_status)
# total responses by religion type
table(d_accept$sr_56_marital_status)
# proportion of total responses, grouped by religion option and level of response variable.
prop.table(table_1, margin=2)
```

#### EDA - Children / no children
```{r eval=T, echo=F, include=T}
# CHILDREN
# Number of records w/ dependents, adult children, and no children
# # 26.3% of resp did not answer question. 777 responses, 278 missing.
# OLR_complete_cases %>% 
#   count(sr_57i_dependents >= 1)  # 274 resp w/ children <18
# OLR_complete_cases %>% 
#   count(sr_57j_adultchildren >= 1)  # 393 resp w/ adult children
# OLR_complete_cases %>% 
#   count(sr_57k_nochildren == 0)  # 110 resp w/ no children



# Collapsing to "children" and "no children"
table_1 <- table(d_accept$sr_12a_actions_contacted_officials, d_accept$children_dumvar)
# total responses by religion type
table(d_accept$children_dumvar)
# proportion of total responses, grouped by religion option and level of response variable.
prop.table(table_1, margin=2)

```
Total number of respondents by "children" and "no children" categories, as well as response proportions. 

#### EDA - Education
Original levels:  
"1"="some high_school", "2"="high_school grad", "3"="somecollege", "4"="Assoc degree", "5"="bachelordeg", "6"="graduatedeg")
Need to combine all Assoc deg or lower options so we have enough responses to analyze.
```{r eval=T, echo=F, include=T}
# EDUCATION
d_accept$sr_61_education <- factor(d_accept$sr_61_education, ordered=TRUE)
# levels(OLR_complete_cases$sr_61_education)
table_1 <- table(d_accept$sr_12a_actions_contacted_officials, d_accept$sr_61_education)
# total responses by religion type
table(d_accept$sr_61_education)
# proportion of total responses, grouped by religion option and level of response variable.
prop.table(table_1, margin=2)
```
 
Reduced levels:  
```{r eval=T, echo=F, include=T}
# Collapsing the following:
# "some HS" and "HS grad" -> "high_school"
# "some college" and "assoc deg" -> "somecollege"
# bach deg and graduate deg stay as-is
d_accept$sr_61_education <- recode_factor(d_accept$sr_61_education, "1"="assocdeg_orlower", "2"="assocdeg_orlower", "3"="assocdeg_orlower", "4"="assocdeg_orlower", "5"="bachelordeg", "6"="graduatedeg")
d_accept$sr_61_education <- ordered(d_accept$sr_61_education)  # put back into order after reducing levels

# levels(OLR_complete_cases$sr_61_education)
table_1 <- table(d_accept$sr_12a_actions_contacted_officials, d_accept$sr_61_education)
# total responses by religion type
table(d_accept$sr_61_education)
# proportion of total responses, grouped by religion option and level of response variable.
prop.table(table_1, margin=2)
```

#### EDA - Employment Status
Original categories:  
"1"="workfulltime", "2"="workparttime", "3"="homemaker", "4"="retired", "5"="student", "6"="unemployed", "0"="other")  
```{r eval=T, echo=F, include=T}
# EMPLOYMENT STATUS
d_accept$sr_71_employment_status <- factor(d_accept$sr_71_employment_status, ordered=FALSE)
# levels(OLR_complete_cases$sr_71_employment_status)
table_1 <- table(d_accept$sr_12a_actions_contacted_officials, d_accept$sr_71_employment_status)
# total responses by religion type
table(d_accept$sr_71_employment_status)
# proportion of total responses, grouped by religion option and level of response variable.
prop.table(table_1, margin=2)
```

Reduced levels:  
Collapsed all other levels into "other" besides "full time work" and "retired" in order to have enough responses to analyze. 
```{r eval=T, echo=F, include=T}
# Collapsing the following: 
# "full-time work" and "retired" stay as-is
# all others -> "other"
d_accept$sr_71_employment_status <- recode_factor(d_accept$sr_71_employment_status, "1"="workfull", "2"="other", "3"="other", "4"="retired", "5"="other", "6"="other", "0"="other")
#levels(OLR_complete_cases$sr_71_employment_status)
table_1 <- table(d_accept$sr_12a_actions_contacted_officials, d_accept$sr_71_employment_status)
# total responses by religion type
table(d_accept$sr_71_employment_status)
# proportion of total responses, grouped by religion option and level of response variable.
prop.table(table_1, margin=2) 
```

#### EDA - Income
Original categories:  
"1"="under25k", "2"="25-49k", "3"="50-74k", "4"="75-99k", "5"="100_150k", "6"="150-199k", "7"="200-249k", "8"="over250k", 9=prefer not to answer
```{r eval=T, echo=F, include=T}
# INCOME
d_accept$sr_72_income <- factor(d_accept$sr_72_income, ordered=TRUE)
# levels(OLR_complete_cases$sr_72_income)
table_1 <- table(d_accept$sr_12a_actions_contacted_officials, d_accept$sr_72_income)
# total responses by religion type
table(d_accept$sr_72_income)
# proportion of total responses, grouped by religion option and level of response variable.
prop.table(table_1, margin=2) 
```

Reduced levels:  
under 100k -> "under100k"  
100-150 -> stays as-is  
over 150 -> "over150k"  
```{r eval=T, echo=F, include=T}
# Collapsing the following:
# "prefer not to answer" -> NA
# under 100k -> "under100k"
# 100-150 -> stays as-is
# over 150 -> "over150k"
d_accept$sr_72_income <- recode_factor(d_accept$sr_72_income, "1"="under100k", "2"="under100k", "3"="under100k", "4"="under100k", "5"="100_150k", "6"="over150k", "7"="over150k", "8"="over150k", "9"="over150k")
d_accept$sr_72_income <- ordered(d_accept$sr_72_income)

# levels(OLR_complete_cases$sr_72_income)[levels(OLR_complete_cases$sr_72_income)=="9"] <- NA
table_1 <- table(d_accept$sr_12a_actions_contacted_officials, d_accept$sr_72_income)
# total responses by religion type
table(d_accept$sr_72_income)
# proportion of total responses, grouped by religion option and level of response variable.
prop.table(table_1, margin=2) 
```


#### EDA - Religion
Reduced levels to religious & non-religious
```{r eval=T, echo=F, include=T}
# RELIGION
table_1 <- table(d_accept$sr_12a_actions_contacted_officials, d_accept$sr_75_religion_dumvar)
# total responses by religion type
table(d_accept$sr_75_religion_dumvar)
# proportion of total responses, grouped by religion option and level of response variable.
prop.table(table_1, margin=2)
```

#### EDA - Political Affiliation
Original levels:  
"1"="democrat", "2"="republican", "3"="independent", "4"="green party", "5"="libertarian", "6"="no party", "0"="other")
```{r eval=T, echo=F, include=T}
# POLITICAL AFFILIATION
d_accept$sr_78_political_affiliation <- factor(d_accept$sr_78_political_affiliation, ordered=FALSE)
# levels(OLR_complete_cases$sr_78_political_affiliation)
table_1 <- table(d_accept$sr_12a_actions_contacted_officials, d_accept$sr_78_political_affiliation)
# total responses by religion type
table(d_accept$sr_78_political_affiliation)
# proportion of total responses, grouped by religion option and level of response variable.
prop.table(table_1, margin=2)
```

Reduced levels:  
```{r eval=T, echo=F, include=T}
# Collapsing as follows:
# "dem" "rep" and "ind" stay as-is
# all others -> "other"
d_accept$sr_78_political_affiliation <- recode_factor(d_accept$sr_78_political_affiliation, "1"="democrat", "2"="republican", "3"="independent", "4"="other", "5"="other", "6"="other", "0"="other")

table_1 <- table(d_accept$sr_12a_actions_contacted_officials, d_accept$sr_78_political_affiliation)
# total responses by religion type
table(d_accept$sr_78_political_affiliation)
# proportion of total responses, grouped by religion option and level of response variable.
prop.table(table_1, margin=2)
```


#### EDA - Political Ideology
Original levels:  
"1"="very liberal", "2"="somewhat liberal", "3"="moderate", "4"="somewhat conservative", "5"="very conservative")
```{r eval=T, echo=F, include=T}
# POLITICAL IDEOLOGY
d_accept$sr_79_political_leaning <- factor(d_accept$sr_79_political_leaning, ordered=FALSE)

table_1 <- table(d_accept$sr_12a_actions_contacted_officials, d_accept$sr_79_political_leaning)
# total responses by religion type
table(d_accept$sr_79_political_leaning)
# proportion of total responses, grouped by religion option and level of response variable.
prop.table(table_1, margin=2)
```

Reduced levels:  
```{r eval=T, echo=F, include=T}
# Collapsing to "liberal" "moderate" "conservative" since we're seeing no differences across the levels. 
d_accept$sr_79_political_leaning <- recode_factor(d_accept$sr_79_political_leaning, "1"="liberal", "2"="liberal", "3"="moderate", "4"="conservative", "5"="conservative")
# levels(OLR_complete_cases$sr_79_political_leaning)
table_1 <- table(d_accept$sr_12a_actions_contacted_officials, d_accept$sr_79_political_leaning)
# total responses by religion type
table(d_accept$sr_79_political_leaning)
# proportion of total responses, grouped by religion option and level of response variable.
prop.table(table_1, margin=2)
```
Collapsing the two liberal levels and two conservative levels into one level apiece. 



## Listwise Deletion
```{r, eval=T, echo=F, include=T}

OLRdata <- d_accept %>% dplyr::select(
  matches("respondent_id"),
  matches("sr_12a_actions_contacted_officials"),
  matches("sr_13a_takeactions_contact_officials"),
  -matches("sr_12a_actions_contacted_officials_factor"),
  matches("descdynamicnorms_comp"),
  matches("desccontactnorms_all_comp"),
  matches("descrolemodelnorms_all_comp"),
  matches("injunctcontactnorms_all_comp"),
  matches("injunctmotivation_all_comp"),
  matches("cimbenefits_comp"),
  matches("cimperceivedrisk_comp"),
  matches("sr_10_harm_you_personally_reversed"),
  matches("sr_11_harm_future_generations_reversed"),
  matches("sr_21a_effective_actions_contacting_officials"),
  matches("efficacy_effectiveness_all_comp"),
  matches("efficacy_competresp_all_comp"),
  matches("behatt_admirablegood_comp"),
  matches("behatt_usefulpleasantsensible_comp"),
  matches("behatt_coolexcitingeasy_comp"),
  matches("sr_7_believe_about_climate_change"),
  matches("sr_30_easy_to_call"),
  matches("sr_31_able_to_call"),
  matches("sr_41a_right_to_modify"),
  matches("sr_41b_laws_of_nature"),
  matches("sr_41c_ingenuity"),
  matches("sr_41d_impotent"),
  matches("sr_41e_govt_do_more"),
  matches("sr_41f_equity"),
  matches("race_white_dumvar"),
  matches("children_dumvar"),
  matches("gender_dumvar"),
  matches("age_true"),
  -matches("age_range"),
  matches("sr_56_marital_status"),
  matches("sr_61_education"),
  matches("sr_71_employment_status"),
  matches("sr_72_income"),
  matches("sr_75_religion_dumvar"),
  matches("sr_78_political_affiliation"),
  matches("sr_79_political_leaning")
)
# listwise deletion
OLR_complete_cases <- OLRdata[complete.cases(OLRdata), ]
dim(OLR_complete_cases)[1] # responses
dim(OLR_complete_cases)[2] # variables

#### Respondents / rejected from d_accept
# Number of respondents / rejects
respondents <- d %>%
  dplyr::filter(reject==0) %>%
  count(respondent_id)

rejected <- d %>%
  dplyr::filter(reject==1) %>%
  count(respondent_id)

write.csv(OLR_complete_cases,"/Users/natebender/Desktop/Repo/RCthesisanalysis/cleandata/perennial_analysis_Apr22.csv", row.names = TRUE)

```

