---
title: "testing-space"
author: "Nate Bender"
date: "4/15/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, eval=TRUE, include=FALSE}
setwd("/Users/natebender/Desktop/Repo/RCthesisanalysis/")
# install.packages("ltm")
library(psych)
library(tidyverse)
library(dplyr)
library(ggplot2)
library(ggfortify)
library(GPArotation)
library(ltm)
library(ggpubr)
```

```{r, include=FALSE}
# Load data, create second dataset of only accepted responses
d <- read.csv("/Users/natebender/Desktop/Graduate_School/Thesis/All-for-1.5/Analysis/dyn_national_20200828 - results-20200930-082116_TEST.csv")

d_accept <- d %>% 
  filter(reject==0)
```

## Principal Components Analysis

### Dynamic Norms
```{r eval=F, include=F}
# Visualize variables
ggscatter(d_accept, x = "sr_24_past_contact", y = "sr_25_future_contact", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Test x", ylab = "Test Y")

shapiro.test(d_accept$sr_24_past_contact)
ggqqplot(d_accept$sr_24_past_contact, ylab = "past contact")

shapiro.test(d_accept$sr_25_future_contact)
ggqqplot(d_accept$sr_25_future_contact, ylab = "future contact")
```

```{r warning=F}
res <- cor.test(d_accept$sr_24_past_contact,d_accept$sr_25_future_contact, method = "spearman")
```
Correlation test of the two dynamic norms items, showing strong pos correlation. Spearman's rho is `r res$estimate` with a p-value of `r res$p.value`.


### Perceived Behavioral Control
```{r warning=F}
res1 <- cor.test(d_accept$sr_30_easy_to_call,d_accept$sr_31_able_to_call, method = "spearman")
```
The two measures of perceived behavioral control show a moderate positive relationship. Spearman's rho is `r res1$estimate` with a p-value of `r res1$p.value`.
