---
title: "Thesis Analysis: National Survey (Aug 3-9, 2020)"
author: "Nate Bender"
date: "5/4/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Packages / Libraries
```{r, eval=TRUE, include=FALSE}
setwd("/Users/natebender/Desktop/Repo/RCthesisanalysis/")
# install.packages("ltm")
# install.packages("fBasics")
# install.packages("ggcorrplot")
library(psych)
library(tidyverse)
library(dplyr)
library(ggplot2)
library(ggfortify)
library(GPArotation)
library(ltm)
library(ggpubr)
library(fBasics)
library(ggcorrplot)
library(car)
```

```{r, include=FALSE}
# Load data, create second dataset of only accepted responses
d <- read.csv("/Users/natebender/Desktop/Graduate_School/Thesis/All-for-1.5/Analysis/dyn_national_20200828 - results-20200930-082116_NEW.csv")

d_accept <- d %>% 
  dplyr::filter(reject == 0)
```

```{r, eval=TRUE, include=FALSE}
# EDA ####
# Number of respondents / rejects
respondents <- d %>% 
  dplyr::filter(reject==0) %>% 
  count(respondent_id)

rejected <- d %>% 
  dplyr::filter(reject==1) %>% 
  count(respondent_id)
```

# Setup / EDA
After filtering the `r count(rejected)` rejected respondents, we're left with `r count(respondents)` valid respondents in the dataset. 

Gender breakdown of respondents is as follows: 
```{r, eval=T, echo=F}
# EDA --IN PROGRESS--
# There are 1055 respondents in d_accept, but I can only find a sum of 1049 respondents across all gender options and I can't find a way to display those skips/"n/a"s???
d_accept %>% 
  summarize(female = sum(gender==1, na.rm = TRUE),
            femalepercent = sum(gender==1, na.rm = TRUE)/sum(gender, na.rm =TRUE),
            male = sum(gender==2, na.rm = TRUE),
            malepercent = sum(gender==2, na.rm = TRUE)/sum(gender, na.rm =TRUE),
            other = sum(gender==3, na.rm = TRUE),
            otherpercent = sum(gender==3, na.rm = TRUE)/sum(gender, na.rm =TRUE),
            noanswer = sum(gender==4, na.rm = TRUE),
            noanswerpercent = sum(gender==4, na.rm = TRUE)/sum(gender, na.rm =TRUE),
            total = sum((gender==1)+(gender==2)+(gender==3)+(gender==4), na.rm = TRUE))
```

```{r, eval=F, include=F, echo=F}
# Early viz and desc stats tables...in progress
for.stats <- d_accept %>% 
  dplyr::select(
    matches("sr_3[a-o]"))

basicStats(for.stats)


ggplot(data = d_accept, aes(x=age)) + geom_bar()

ggplot(data = d_accept, aes(x=gender)) + geom_bar()

ggplot(data = for.stats, aes(x=sr_3a_importance_abortion)) + geom_bar()


cormatdesccontactnorms <- d_pca_descriptivecontactnorms %>%
  cor(., use = "pairwise.complete.obs")

ggcorrplot(cormatdesccontactnorms, # correlation matrix
           type = "lower", # print the lower part of the correlation matrix
           hc.order = TRUE, # hierarchical clustering of correlations
           lab = TRUE) # add correlation values as labels
```

# Principal Components Analysis
$$\\[.05in]$$

### Dynamic Norms
*"Do you think that over the PAST/NEXT 12 months the percentage of adults in the United States who contacted elected officials to urge them to take action to reduce global warming is..."*   

One factor solution:   
1. Two-item factor consisting of the two dynamic norms questions (changes in the number of ppl contacting reps in the past and future)

```{r eval=F, include=F}
# Visualize variables
# *** Need to address errors in this visualization code ***

ggscatter(d_accept, x = "sr_24_past_contact", y = "sr_25_future_contact", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Test x", ylab = "Test Y")

shapiro.test(d_accept$sr_24_past_contact)
ggqqplot(d_accept$sr_24_past_contact, ylab = "past contact")

shapiro.test(d_accept$sr_25_future_contact)
ggqqplot(d_accept$sr_25_future_contact, ylab = "future contact")
```

```{r, eval=T, echo=F, warning=F}
res <- cor.test(d_accept$sr_24_past_contact,d_accept$sr_25_future_contact, method = "spearman")
print(res)

mean(d_accept$sr_24_past_contact, na.rm=TRUE)
sd(d_accept$sr_24_past_contact, na.rm=TRUE)

mean(d_accept$sr_25_future_contact, na.rm=TRUE)
sd(d_accept$sr_25_future_contact, na.rm=TRUE)
```
Correlation test of the two dynamic norms items shows strong positive correlation, with Spearman's rho of `r res$estimate` and p-value of `r res$p.value`.

$$\\[.05in]$$

### Descriptive Norms (contact)
*"To what extent do you think that the following people ARE CONTACTING (writing letters, emailing, or calling) their elected representatives in Congress to urge action on reducing climate change?"*

Three factor solution (70% cumulative variance (hereafter: cv))   
1. 1-item variable: Parents   
2. 2-item composite variable: Spouse, Children   
3. Multi-item composite variable: Non-immediate family

```{r, eval=T, echo=F}
d_pca_descriptivecontactnorms <- d_accept %>% 
  dplyr::select(
    matches("sr_19a"),
    matches("sr_19b"),
    matches("sr_19c"),
    matches("sr_19d"),
    matches("sr_19e"),
    matches("sr_19f"),
    matches("sr_19g"),
    matches("sr_19h"))
    
fa.parallel(d_pca_descriptivecontactnorms, fm='minres', fa='fa')
pca1 <- fa(d_pca_descriptivecontactnorms, nfactors = 4, rotate = "Varimax", fm="minres") 
print(pca1)
print(pca1$loadings,cutoff = 0.3)
```

#### Descriptive Norms (contact) - 1st factor (Parents) - desc stats
```{r, eval=T, echo=F}
mean(d_accept$sr_19a_contacting_officials__parents, na.rm=TRUE)
sd(d_accept$sr_19a_contacting_officials__parents, na.rm=TRUE)

summary(d_pca_descriptivecontactnorms)
sapply(d_pca_descriptivecontactnorms, sd, na.rm=TRUE)
```

#### Descriptive Norms (contact) - 2nd factor (Spouse & Children) - Correlation & desc stats
```{r, eval=T, echo=F}
res <- cor.test(d_accept$sr_19b_contacting_officials_spouse,d_accept$sr_19c_contacting_officials_children, method = "spearman", exact=FALSE)
print(res)

mean(d_accept$sr_19b_contacting_officials_spouse, na.rm=TRUE)
sd(d_accept$sr_19b_contacting_officials_spouse, na.rm=TRUE)

mean(d_accept$sr_19c_contacting_officials_children, na.rm=TRUE)
sd(d_accept$sr_19c_contacting_officials_children, na.rm=TRUE)
```
Correlation test of the two descriptive norms items for Spouse and Children, showing moderate positive correlation. Spearman's rho is `r res$estimate` with a p-value of `r res$p.value`.

#### Descriptive Norms (contact) - 3rd factor (Non-immediate family) - Cronbach Alpha
```{r, eval=T, echo=F}
d_pca_descriptivecontactnormsnonfamily <- d_accept %>% 
  dplyr::select(
    matches("sr_19d"),
    matches("sr_19e"),
    matches("sr_19f"),
    matches("sr_19g"),
    matches("sr_19h"))

psych::alpha(d_pca_descriptivecontactnormsnonfamily, use ="pairwise", na.rm = TRUE) 


```

$$\\[.05in]$$

### Descriptive Norms (role models)
*"How likely are you to consider each of these groups as behavioral role models?"*

Scree plot suggests four factors (78% cumulative var), but three factor solution makes the most sense.   
Three factor solution (71% cv):   
1. 1-item variable: Parents   
2. 2-item composite variable: Spouse, Children   
3. Multi-item composite variable: Non-immediate family

```{r eval=TRUE, echo=F}
d_pca_descriptiverolemodelnorms <- d_accept %>% 
  dplyr::select(
    matches("sr_20a"),
    matches("sr_20b"),
    matches("sr_20c"),
    matches("sr_20d"),
    matches("sr_20e"),
    matches("sr_20f"),
    matches("sr_20g"),
    matches("sr_20h"))
    
fa.parallel(d_pca_descriptiverolemodelnorms, fm='minres', fa='fa')
pca1 <- fa(d_pca_descriptiverolemodelnorms, nfactors = 4, rotate = "Varimax", fm="minres") 
print(pca1)
print(pca1$loadings,cutoff = 0.3) 
```

#### Descriptive Norms (role models) - 1st factor (Parents) - Descriptive stats
```{r, eval=T, echo=F}
mean(d_accept$sr_20a_rolemodels_parents, na.rm=TRUE)
sd(d_accept$sr_20a_rolemodels_parents, na.rm=TRUE)
```


#### Descriptive Norms (role models) - 2nd factor (Spouse & Children) - Correlation
```{r, eval=T, echo=F}
res <- cor.test(d_accept$sr_20b_rolemodels_spouse,d_accept$sr_20c_rolemodels_children, method = "spearman", exact=FALSE)
print(res)

mean(d_accept$sr_20b_rolemodels_spouse, na.rm=TRUE)
sd(d_accept$sr_20b_rolemodels_spouse, na.rm=TRUE)

mean(d_accept$sr_20c_rolemodels_children, na.rm=TRUE)
sd(d_accept$sr_20c_rolemodels_children, na.rm=TRUE)
```
Correlation test of the two descriptive norms items for Spouse and Children, showing moderate positive correlation. Spearman's rho is `r res$estimate` with a p-value of `r res$p.value`.

#### Descriptive Norms (role models) - 3rd factor (Non-immediate family) - Cronbach Alpha
```{r, eval=T, echo=F}
d_pca_descriptiverolemodelnormsnonfamily <- d_accept %>% 
  dplyr::select(
    matches("sr_20d"),
    matches("sr_20e"),
    matches("sr_20f"),
    matches("sr_20g"),
    matches("sr_20h"))

psych::alpha(d_pca_descriptiverolemodelnormsnonfamily, use ="pairwise", na.rm = TRUE) 

summary(d_pca_descriptivecontactnormsnonfamily)
sapply(d_pca_descriptivecontactnormsnonfamily, sd, na.rm=TRUE)
```

$$\\[.05in]$$

### Injunctive Norms (contact) 
*"To what extent do you think that the following people EXPECT YOU to contact (writing letters, emailing, or calling) your elected representatives to urge action on reducing climate change?"*

Scree plot suggests four factors (78% cv) but three (73% cv) makes the most sense.     
Three-factor solution:   
1. 1-item variable: Parents   
2. 2-item composite variable: Spouse, Children   
3. Multi-item composite variable: Non-immediate family

```{r, eval=T, echo=F}
d_pca_injunctivecontactnorms <- d_accept %>% 
  dplyr::select(
    matches("sr_22a"),
    matches("sr_22b"),
    matches("sr_22c"),
    matches("sr_22d"),
    matches("sr_22e"),
    matches("sr_22f"),
    matches("sr_22g"),
    matches("sr_22h"))

fa.parallel(d_pca_injunctivecontactnorms, fm='minres', fa='fa')
pca1 <- fa(d_pca_injunctivecontactnorms, nfactors = 4, rotate = "Varimax", fm="minres") 
print(pca1)
print(pca1$loadings,cutoff = 0.3)

summary(d_pca_injunctivecontactnorms)
sapply(d_pca_injunctivecontactnorms, sd, na.rm=TRUE)
```

#### Injunctive Norms (contact) - 2nd factor (Spouse & Children) - Correlation
```{r, eval=T, echo=F}
res <- cor.test(d_accept$sr_22b_expect_contact_spouse,d_accept$sr_22c_expect_contact_children, method = "spearman", exact=FALSE)
print(res)
```
Correlation test of the two descriptive norms items for Spouse and Children, showing moderate positive correlation. Spearman's rho is `r res$estimate` with a p-value of `r res$p.value`.

#### Injunctive Norms (contact) - 3rd factor (Non-family) - Cronbach Alpha
```{r, eval=T, echo=F}
d_pca_injunctivecontactnormsnonfamily <- d_accept %>% 
  dplyr::select(
    matches("sr_22d"),
    matches("sr_22e"),
    matches("sr_22f"),
    matches("sr_22g"),
    matches("sr_22h"))

psych::alpha(d_pca_injunctivecontactnormsnonfamily, use ="pairwise", na.rm = TRUE) 
```
$$\\[.05in]$$

### Injunctive Norms (compliance)
*"How motivated are you to comply with the expectations of each of these people?"*

Two factor solution (70% cv)    
1. Multi-item composite variable: Parents, Spouse, Children   
2. Multi-item composite variable: Otherfam, Friends, Cowork, Recpartners, Faith

```{r, eval=T, echo=F}
d_pca_injunctivecompliance <- d_accept %>% 
  dplyr::select(
    matches("sr_23a"),
    matches("sr_23b"),
    matches("sr_23c"),
    matches("sr_23d"),
    matches("sr_23e"),
    matches("sr_23f"),
    matches("sr_23g"),
    matches("sr_23h"))

fa.parallel(d_pca_injunctivecompliance, fm='minres', fa='fa')
pca1 <- fa(d_pca_injunctivecompliance, nfactors = 2, rotate = "Varimax", fm="minres") 
print(pca1)
print(pca1$loadings,cutoff = 0.3)

summary(d_pca_injunctivecompliance)
sapply(d_pca_injunctivecompliance, sd, na.rm=TRUE)
```

#### Injunctive Norms (compliance) - 1st factor (Immediate Family) - Cronbach Alpha
```{r, eval=T, echo=F}
d_pca_injunctivecompliancefamily <- d_accept %>% 
  dplyr::select(
    matches("sr_23a"),
    matches("sr_23b"),
    matches("sr_23c"))

psych::alpha(d_pca_injunctivecompliancefamily, use ="pairwise", na.rm = TRUE) 
```

#### Injunctive Norms (compliance) - 2nd factor (Non-family) - Cronbach Alpha
```{r, eval=T, echo=F}
d_pca_injunctivecompliancenonfamily <- d_accept %>% 
  dplyr::select(
    matches("sr_23d"),
    matches("sr_23e"),
    matches("sr_23f"),
    matches("sr_23g"),
    matches("sr_23h"))

psych::alpha(d_pca_injunctivecompliancenonfamily, use ="pairwise", na.rm = TRUE) 
```

$$\\[.05in]$$

### CIM - Benefits
*"How often do you hear ____ talk about the importance of reducing climate change?"*   
*[your friends, family, and coworkers]*   
*[public figures whom you respect]*   
*[about the importance of reducing climate change in the media? (TV, movies, radio, newspapers/news websites, magazines, etc.)]*

One-factor solution:   
1. Multi-item composite variable: F/Fam/Cowork, Public Figures, Media

```{r, eval=T, echo=F}
d_pca_CIMbenefits <- d_accept %>% 
  dplyr::select(
    matches("sr_16"),
    matches("sr_17"),
    matches("sr_18"))

fa.parallel(d_pca_CIMbenefits, fm='minres', fa='fa')
pca1 <- fa(d_pca_CIMbenefits, nfactors = 1, rotate = "Varimax", fm="minres") 
print(pca1)
print(pca1$loadings,cutoff = 0.3)
```

#### CIM - Benefits - Cronbach Alpha
```{r, eval=T, echo=F}
psych::alpha(d_pca_CIMbenefits, use ="pairwise", na.rm = TRUE) 
```

$$\\[.05in]$$

### CIM - Perceived Risk
*"How important is each of the following issues to you today?"*   
*"How important is the issue of climate change to you personally?"*   
*"How worried are you about climate change?"*   
*"How much do you think climate change will harm you personally?"*   
*"How much do you think climate change will harm future generations of people?"*

NOTE - removing #7 for now until I understand how to properly account for it. 

Three-factor solution   
1. Multi-item composite variable: CC importance as an issue, CC personal importance, CC worry, belief of personal harm from CC    
2. 1-item variable: anthropocentric CC belief
3. 1-item variable: belief of harm to future generations from CC

```{r, eval=T, echo=F}
d_pca_CIMperceivedrisk <- d_accept %>% 
  dplyr::select(
    matches("sr_3b_importance_climatechange"),
    matches("sr_8_importance_personally"),
    matches("sr_9_worried"),
    matches("sr_10_harm_you_personally"),
    matches("sr_11_harm_future_generations"))

fa.parallel(d_pca_CIMperceivedrisk, fm='minres', fa='fa')
pca1 <- fa(d_pca_CIMperceivedrisk, nfactors = 2, rotate = "Varimax", fm="minres") 
print(pca1)
print(pca1$loadings,cutoff = 0.3)
```

#### CIM - Perceived Risk - 1st factor (Personal) - Cronbach Alpha
```{r, eval=T, echo=F}
d_pca_CIMperceivedriskpersonal <- d_accept %>% 
  dplyr::select(
    matches("sr_3b_importance_climatechange"),
    matches("sr_8_importance_personally"),
    matches("sr_9_worried"),
    matches("sr_10_harm_you_personally"))

psych::alpha(d_pca_CIMperceivedriskpersonal, use ="pairwise", na.rm = TRUE) 
```

#### CIM - Perceived Risk - Descriptive stats on single-item variables
```{r, eval=T, echo=T}

mean(d_accept$sr_11_harm_future_generations, na.rm=TRUE)
sd(d_accept$sr_11_harm_future_generations, na.rm=TRUE)

mean(d_accept$sr_7_believe_about_climate_change, na.rm=TRUE)
sd(d_accept$sr_7_believe_about_climate_change, na.rm=TRUE)

```
$$\\[.05in]$$

### Efficacy
*"Below is a list of actions that individuals could take to reduce climate change. If YOU took these actions, how effective would each be for reducing climate change?"*   
*"Below are some public and private organizations who make decisions that have an impact on climate change. In general, how COMPETENT is each in addressing climate change?"*   
*"In general, how RESPONSIVE is each in addressing climate change?"*   
*"How much do you agree that each type of organization is generally IN A POSITION TO EFFECTIVELY reduce climate change?"* 

Three-factor solution:   
1. 1-item variable: 21a: Is contacting elected reps an effective action?   
2. Multi-item composite variable: All types (fed, state, business, ngo) are in a position to effect change   
3. Multi-item composite variable: The competency and responsiveness of fed, state, and business   
4. 2-item composite variable: The competency and responsiveness of ngo only

```{r, eval=T, echo=F}
d_pca_efficacysecond <- d_accept %>% 
  dplyr::select(
    matches("sr_27[a-d]"),
    matches("sr_28[a-d]"),
    matches("sr_29[a-d]"))

fa.parallel(d_pca_efficacysecond, fm='minres', fa='fa')
pca1 <- fa(d_pca_efficacysecond, nfactors = 3, rotate = "Varimax", fm="minres") 
print(pca1)
print(pca1$loadings,cutoff = 0.3)
```

#### Efficacy - 1st variable (contacting elected officials an effective action?)
```{r, eval=T, echo=F}
mean(d_accept$sr_21a_effective_actions_contacting_officials, na.rm=TRUE)
sd(d_accept$sr_21a_effective_actions_contacting_officials, na.rm=TRUE)
```

#### Efficacy - 2nd Factor (All types' ability to effect change) - Cronbach Alpha 
```{r, eval=T, echo=F}
d_pca_efficacyeffectchangesecond <- d_accept %>% 
  dplyr::select(
    matches("sr_29[a-d]"))

psych::alpha(d_pca_efficacyeffectchangesecond, use ="pairwise", na.rm = TRUE) 
```

#### Efficacy - 3rd Factor (Competency & Responsiveness of Fed, State, and Business) - Cronbach Alpha 
```{r, eval=T, echo=F}
d_pca_efficacycompetencyresponsivesecond <- d_accept %>% 
  dplyr::select(
    matches("sr_27[a-c]"),
    matches("sr_28[a-c]"))

psych::alpha(d_pca_efficacycompetencyresponsivesecond, use ="pairwise", na.rm = TRUE) 
```

#### Efficacy - 4th Factor (Competency & Responsiveness of NGO) - Correlation 
```{r, eval=T, echo=F}
res <- cor.test(d_accept$sr_27d_competent_ngo,d_accept$sr_28d_responsive_ngo, method = "spearman", exact=FALSE)
print(res)

mean(d_accept$sr_27d_competent_ngo, na.rm=TRUE)
sd(d_accept$sr_27d_competent_ngo, na.rm=TRUE)

mean(d_accept$sr_28d_responsive_ngo, na.rm=TRUE)
sd(d_accept$sr_28d_responsive_ngo, na.rm=TRUE)
```
Correlation test of the competency and responsiveness scores for NGOs shows moderate positive correlation. Spearman's rho is `r res$estimate` with a p-value of `r res$p.value`.  

$$\\[.05in]$$

### TPB Behavioral Attitude
*"For me, contacting (writing letters, emailing, phoning my elected representatives in Congress to urge action on climate change on a regular basis during the next year would be …"*

Three-factor solution:   
1. Multi-item composite variable: cool/uncool, admirable/shameful, good/bad, exciting/boring   
2. Multi-item composite variable: useful/useless, pleasant/intimidating, sensible/foolish  
3. 1-item variable: easy/awkward   

```{r, eval=F, echo=F, include=F}
d_pca_behavioralattitude <- d_accept %>% 
    dplyr::select(-"sr_32_contact_useful_reversed") %>% 
    dplyr::select(-"sr_33_contact_pleasant_reversed") %>% 
    dplyr::select(-"sr_37_contact_foolish_reversed") %>% 
  dplyr::select(
    matches("sr_32"),
    matches("sr_33"),
    matches("sr_34"),
    matches("sr_35"),
    matches("sr_36"),
    matches("sr_37"),
    matches("sr_38"),
    matches("sr_39"))


fa.parallel(d_pca_behavioralattitude, fm='minres', fa='fa')
pca1 <- fa(d_pca_behavioralattitude, nfactors = 3, rotate = "Varimax", fm="minres") 
print(pca1)
print(pca1$loadings,cutoff = 0.3)
```

```{r, eval=T, echo=F}
d_accept <- d_accept %>% 
  mutate(sr_32_contact_useful_reversed = car::recode(sr_32_contact_useful, "1=6 ; 2=5 ; 3=4 ; 4=3 ; 5=2 ; 6=1")) 

d_accept <- d_accept %>% 
  mutate(sr_33_contact_pleasant_reversed = car::recode(sr_33_contact_pleasant, "1=6 ; 2=5 ; 3=4 ; 4=3 ; 5=2 ; 6=1"))

d_accept <- d_accept %>%
  mutate(sr_37_contact_foolish_reversed = car::recode(sr_37_contact_foolish, "1=6 ; 2=5 ; 3=4 ; 4=3 ; 5=2 ; 6=1"))

ba2 <- d_accept %>% 
  dplyr::select(
    matches("sr_32_contact_useful_reversed"),
    matches("sr_33_contact_pleasant_reversed"),
    matches("sr_34"),
    matches("sr_35"),
    matches("sr_36"),
    matches("sr_37_contact_foolish_reversed"),
    matches("sr_38"),
    matches("sr_39"))


fa.parallel(ba2, fm='minres', fa='fa')
pca1 <- fa(ba2, nfactors = 3, rotate = "Varimax", fm="minres") 
print(pca1)
print(pca1$loadings,cutoff = 0.3)
```

#### TPB Behavioral Attitude - 1st factor - Correlation
```{r, eval=T, echo=F}
res <- cor.test(d_accept$sr_38_contact_admirable,d_accept$sr_39_contact_good, method = "spearman")
print(res)
```
The two measures of perceived behavioral control show a moderate positive relationship, just barely under the .65 rule of thumb. Spearman's rho is `r res$estimate` with a p-value of `r res$p.value`.   


#### TPB Behavioral Attitude - 2nd factor - Cronbach Alpha
```{r, eval=T, echo=F}
d_pca_behavioralattitude2 <- d_accept %>% 
  dplyr::select(
    matches("sr_32_contact_useful_reversed"),
    matches("sr_33_contact_pleasant_reversed"),
    matches("sr_37_contact_foolish_reversed"))

psych::alpha(d_pca_behavioralattitude2, use ="pairwise", na.rm = TRUE) 
```

#### TPB Behavioral Attitude - 3rd factor - Cronbach Alpha
```{r, eval=T, echo=F}
d_pca_behavioralattitude3 <- d_accept %>% 
  dplyr::select(
    matches("sr_34"),
    matches("sr_35"),
    matches("sr_36"))

psych::alpha(d_pca_behavioralattitude3, use ="pairwise", na.rm = TRUE) 
```

$$\\[.05in]$$
#### Perceived Behavioral Control - correlation
```{r, eval=T, echo=F, warning=F}
mean(d_accept$sr_35_contact_easy, na.rm=TRUE)
sd(d_accept$sr_35_contact_easy, na.rm=TRUE)
```

### Perceived Behavioral Control
```{r, eval=T, echo=F, warning=F}
res <- cor.test(d_accept$sr_30_easy_to_call,d_accept$sr_31_able_to_call, method = "spearman")
print(res)

mean(d_accept$sr_30_easy_to_call, na.rm=TRUE)
sd(d_accept$sr_30_easy_to_call, na.rm=TRUE)

mean(d_accept$sr_31_able_to_call, na.rm=TRUE)
sd(d_accept$sr_31_able_to_call, na.rm=TRUE)
```
The two measures of perceived behavioral control show a moderate positive relationship, just barely under the .65 rule of thumb. Spearman's rho is `r res$estimate` with a p-value of `r res$p.value`. This is not a strong enough correlation to justify a composite variable of the two items, so they will stay separate.

$$\\[.05in]$$

### Worldviews
We decided these will be kept as-is.

```{r, eval=T, echo=F}
d_worldviews <- d_accept %>% 
  dplyr::select(
    matches("sr_41a"),
    matches("sr_41b"),
    matches("sr_41c"),
    matches("sr_41d"),
    matches("sr_41e"),
    matches("sr_41f"))

summary(d_worldviews)
sapply(d_worldviews, sd, na.rm=TRUE)
```
$$\\[.05in]$$


### CIM - Costs
The variables included in this CIM Costs category currently are:   
1. Age   
2. Gender   
3. # of dependents (<18 years old)   
4. # of adult children (>=18 years old)   
5. Race (1=white selected, 0=all other ethnicities, or white+ethnicity)  
6. Level of education completed   
7. Employment status   
8. Total 2019 annual income   
9. Political affiliation   
10. Political leaning   

```{r, eval=F, include=F}
# Number of records w/ dependents, adult children, and no children
d_accept %>% 
  count(sr_57i_dependents >= 1)

d_accept %>% 
  count(sr_57j_adultchildren >= 1)

d_accept %>% 
  count(sr_57k_nochildren == 0)

# Create dummy variables for race. 1=white, 0=all others; check accuracy of variable
d_accept %>%
  mutate(race_white_dumvar = ifelse(d_accept$sr_74_1_race_white==1 & is.na(d_accept$sr_74_2_race_black) & is.na(d_accept$sr_74_3_race_hispanic) & is.na(d_accept$sr_74_4_race_native_american) & is.na(d_accept$sr_74_5_race_east_asian) & is.na(d_accept$sr_74_6_race_middle_eastern) & is.na(d_accept$sr_74_7_race_south_asian),1,0)) %>%
  dplyr::select(sr_74_1_race_white, sr_74_2_race_black, sr_74_3_race_hispanic, sr_74_4_race_native_american, sr_74_5_race_east_asian, sr_74_6_race_middle_eastern, sr_74_7_race_south_asian, race_white_dumvar) %>% 
  arrange(desc(race_white_dumvar)) %>% 
  head(10)

# number of white respondents
sum(d_accept$sr_74_1_race_white==1, na.rm = T)
# number of other ethnicities
sum(d_accept$sr_74_2_race_black==2 | d_accept$sr_74_3_race_hispanic==3 | d_accept$sr_74_4_race_native_american==4 | d_accept$sr_74_5_race_east_asian==5 | d_accept$sr_74_6_race_middle_eastern==6 | d_accept$sr_74_7_race_south_asian==7, na.rm = T)
  
```

# Creating PCA variables for regression
```{r, eval=T, include=T}
# Dynamic, descriptive, and injunctive norms
d_accept <- d_accept %>% 
  mutate(
    descdynamicnorms_comp = rowMeans(subset(d_accept, select = c(sr_24_past_contact, sr_25_future_contact)), na.rm = T),
    desccontactnorms_fam_comp = rowMeans(subset(d_accept, select = c(sr_19b_contacting_officials_spouse, sr_19c_contacting_officials_children)), na.rm = T),
    desccontactnorms_nf_comp = rowMeans(subset(d_accept, select = c(sr_19d_contacting_officials_otherfamily, sr_19e_contacting_officials_friends, sr_19f_contacting_officials_coworkers, sr_19g_contacting_officials_recpartners, sr_19h_contacting_officials_faithcommun)), na.rm=T),
    descrolemodelnorms_fam_comp = rowMeans(subset(d_accept, select = c(sr_20b_rolemodels_spouse, sr_20c_rolemodels_children)), na.rm = T),
    descrolemodelnorms_nf_comp = rowMeans(subset(d_accept, select = c(sr_20d_rolemodels_otherfamily, sr_20e_rolemodels_friends, sr_20f_rolemodels_coworkers, sr_20g_rolemodels_recpartners, sr_20h_rolemodels_faithcommun)), na.rm=T),
    injunctcontactnorms_fam_comp = rowMeans(subset(d_accept, select = c(sr_22b_expect_contact_spouse, sr_22c_expect_contact_children)), na.rm = T),
    injunctcontactnorms_nf_comp = rowMeans(subset(d_accept, select = c(sr_22d_expect_contact_otherfamily, sr_22e_expect_contact_friends, sr_22f_expect_contact_coworkers, sr_22g_expect_contact_recpartners, sr_22h_expect_contact_faithcommun)), na.rm=T),
    injunctmotivation_fam_comp = rowMeans(subset(d_accept, select = c(sr_23a_motivated_to_comply_parents, sr_23b_motivated_to_comply_spouse,sr_23c_motivated_to_comply_children)), na.rm = T),
    injunctmotivation_nf_comp = rowMeans(subset(d_accept, select = c(sr_23d_motivated_to_comply_otherfamily, sr_23e_motivated_to_comply_friends, sr_23f_motivated_to_comply_coworkers, sr_23g_motivated_to_comply_recpartners, sr_23h_motivated_to_comply_faithcommun)), na.rm = T),
      )

# CIM - Benefits
d_accept <- d_accept %>% 
  mutate(
    cimbenefits_comp = rowMeans(subset(d_accept, select = c(sr_16_hear_friends_talk, sr_17_hear_media, sr_18_hear_public_officials)), na.rm = T))

# CIM - Perceived Risk
d_accept <- d_accept %>% 
  mutate(
    cimperceivedrisk_comp = rowMeans(subset(d_accept, select = c(sr_3a_importance_abortion, sr_8_importance_personally, sr_9_worried, sr_10_harm_you_personally)), na.rm = T))

# Efficacy
d_accept <- d_accept %>% 
  mutate(
    efficacy_effectiveness_comp = rowMeans(subset(d_accept, select = c(sr_29a_effective_fed, sr_29b_effective_state, sr_29c_effective_business, sr_29d_effective_ngo)), na.rm = T),
    efficacy_fedstatebusiness_competresp_comp = rowMeans(subset(d_accept, select = c(sr_27a_competent_fed, sr_27b_competent_state, sr_27c_competent_business, sr_28a_responsive_fed, sr_28b_responsive_state, sr_28c_responsive_business)), na.rm = T),
    efficacy_ngo_competresp_comp = rowMeans(subset(d_accept, select = c(sr_27d_competent_ngo, sr_28d_responsive_ngo)), na.rm = T)
    )

# TPB - Behavioral Attitude
d_accept <- d_accept %>% 
  mutate(
    behatt_admirablegood_comp = rowMeans(subset(d_accept, select = c(sr_38_contact_admirable, sr_39_contact_good)), na.rm = T),
    behatt_usefulpleasantsensible_comp = rowMeans(subset(d_accept, select = c(sr_32_contact_useful_reversed, sr_33_contact_pleasant_reversed, sr_37_contact_foolish_reversed)), na.rm = T),
    behatt_coolexcitingeasy_comp = rowMeans(subset(d_accept, select = c(sr_34_contact_cool, sr_35_contact_easy, sr_36_contact_exciting)), na.rm = T)
    )

# test to make sure variable-creation code is working
d_accept %>% 
  dplyr::select(sr_32_contact_useful_reversed, sr_33_contact_pleasant_reversed, sr_37_contact_foolish_reversed, behatt_usefulpleasantsensible_comp)

```
