---
title: "Thesis Analysis: National Survey (Aug 3-9, 2020)"
author: "Nate Bender"
date: "5/4/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#### Packages / Libraries
```{r, eval=TRUE, include=FALSE}
setwd("/Users/natebender/Desktop/Repo/RCthesisanalysis/")
# install.packages("ltm")
# install.packages("fBasics")
# install.packages("ggcorrplot")
# install.packages("fastDummies")

library(psych)
library(tidyverse)
library(dplyr)
library(ggplot2)
library(ggfortify)
library(GPArotation)
library(ltm)
library(ggpubr)
library(fBasics)
library(ggcorrplot)
library(car)
library(fastDummies)
```

#### Load data, filter rejected out
```{r, include=FALSE}
# Load data, create second dataset of only accepted responses
d <- read.csv("/Users/natebender/Desktop/Graduate_School/Thesis/All-for-1.5/Analysis/dyn_national_20200828 - results-20200930-082116_NEW.csv")

d_accept <- d %>% 
  dplyr::filter(reject == 0)

# Check structure of variables, if needed 
# str(d_accept, list.len=ncol(d_accept))
```


### EDA
#### Respondents / rejected
```{r, eval=TRUE, include=TRUE}
# Number of respondents / rejects
respondents <- d %>% 
  dplyr::filter(reject==0) %>% 
  count(respondent_id)

rejected <- d %>% 
  dplyr::filter(reject==1) %>% 
  count(respondent_id)
```
After filtering the `r count(rejected)` rejected respondents, we're left with `r count(respondents)` valid respondents. 

#### DVs: 
```{r, eval=T, echo=F}
# EDA --IN PROGRESS--

plot <- ggplot(data = d_accept, na.rm=TRUE) +
  geom_bar(mapping = aes(x = sr_12a_actions_contacted_officials))


ggplot(data = d_accept) +
  geom_bar(mapping = aes(x = sr_12a_actions_contacted_officials)) +
  scale_x_continuous(breaks = c(1, 2, 3), labels = c("Never", "Once in last year", "More than once"))


ggplot(data = d_accept) +
  geom_bar(mapping = aes(x = sr_13a_takeactions_contact_officials)) +
  scale_x_continuous(breaks = c(1, 2, 3, 4, 5), labels = c("1" = "test1", "2" = "test2", "3" = "test3", "4" = "test4", "5" = "test5"))
```
```{r, eval=T, echo=F}
# Missing values across the entire d_accept
# colSums(is.na(d_accept))

# Percentages of missing data by variable
missingpercentages <- function(x) {sum(is.na(x))/length(x)*100}
apply(d_accept, 2, missingpercentages)

# Check missing values for only variables used in OLR, NOT INCLUDING THE VARS USED IN THE FACTOR ANALYSIS

OLRorigvarsmissing <- d_accept %>% dplyr::select(
  matches("sr_12a_actions_contacted_officials"), 
  matches("gender"),
  matches("age"),
  -matches("age_range"),
  matches("race_present_dumvar"),
  matches("children_responded"),
  matches("sr_19a_contacting_officials__parents"),
  matches("sr_20a_rolemodels_parents"),
  matches("sr_22a_expect_contact_parents"),
  matches("sr_7_believe_about_climate_change"),
  matches("sr_11_harm_future_generations"),
  matches("sr_21a_effective_actions_contacting_officials"),
  matches("sr_30_easy_to_call"),
  matches("sr_31_able_to_call"),
  matches("sr_41a_right_to_modify"),
  matches("sr_41b_laws_of_nature"),
  matches("sr_41c_ingenuity"),
  matches("sr_41d_impotent"),
  matches("sr_41e_govt_do_more"),
  matches("sr_41f_equity"),
  matches("sr_56_marital_status"),
  matches("sr_61_education"),
  matches("sr_71_employment_status"),
  matches("sr_72_income"),
  matches("sr_78_political_affiliation"),
  matches("sr_79_political_leaning")
)
p_missing <- unlist(lapply(OLRorigvarsmissing, function(x) sum(is.na(x))))/nrow(d_accept)
sort(p_missing[p_missing > 0], decreasing = TRUE)


```

```{r eval=T, echo=F}
# all of my composite variables are incorrect because they were calculated with missing values in place. 
# 2 missing values for past contact, 3 for future contact. But the comp variable has 1055 observations, meaning the code I created just ignored any NAs and found the average anyway.
# So I bet if there was a 3 for one observation and an NA for that respondent on the other variable, the comp var got a 1.5

d_accept %>% count(sr_24_past_contact >0)
d_accept %>% count(sr_25_future_contact >0)
d_accept %>% count(descdynamicnorms_comp)




```


```{r eval=T, echo=F}
# Checking missing values in all original vars that went into factor analysis and subsequently into composite variables.

OLRcompvarsmissing <- d_accept %>% dplyr::select(
  matches("sr_24_past_contact"),
  matches("sr_25_future_contact"),
  
  matches("sr_19b_contacting_officials_spouse"),
  matches("sr_19c_contacting_officials_children"),

  matches("sr_19d_contacting_officials_otherfamily"),
  matches("sr_19e_contacting_officials_friends"),
  matches("sr_19f_contacting_officials_coworkers"),
  matches("sr_19g_contacting_officials_recpartners"),
  matches("sr_19h_contacting_officials_faithcommun"),

  matches("sr_20b_rolemodels_spouse"),
  matches("sr_20c_rolemodels_children"),

  matches("sr_20d_rolemodels_otherfamily"),
  matches("sr_20e_rolemodels_friends"),
  matches("sr_20f_rolemodels_coworkers"),
  matches("sr_20g_rolemodels_recpartners"),
  matches("sr_20h_rolemodels_faithcommun"),

  matches("sr_22b_expect_contact_spouse"),
  matches("sr_22c_expect_contact_children"),

  matches("sr_22d_expect_contact_otherfamily"),
  matches("sr_22e_expect_contact_friends"),
  matches("sr_22f_expect_contact_coworkers"),
  matches("sr_22g_expect_contact_recpartners"),
  matches("sr_22h_expect_contact_faithcommun"),

  matches("sr_23a_motivated_to_comply_parents"),
  matches("sr_23b_motivated_to_comply_spouse"),
  matches("sr_23c_motivated_to_comply_children"),

  matches("sr_23d_motivated_to_comply_otherfamily"),
  matches("sr_23e_motivated_to_comply_friends"),
  matches("sr_23f_motivated_to_comply_coworkers"),
  matches("sr_23g_motivated_to_comply_recpartners"),
  matches("sr_23h_motivated_to_comply_faithcommun"),

  matches("sr_16_hear_friends_talk"),
  matches("sr_17_hear_media"),
  matches("sr_18_hear_public_officials"),

  matches("sr_3a_importance_abortion"),
  matches("sr_8_importance_personally"),
  matches("sr_9_worried"),
  matches("sr_10_harm_you_personally"),

  matches("sr_29a_effective_fed"),
  matches("sr_29b_effective_state"),
  matches("sr_29c_effective_business"),
  matches("sr_29d_effective_ngo"),

  matches("sr_27a_competent_fed"),
  matches("sr_27b_competent_state"),
  matches("sr_27c_competent_business"),
  matches("sr_28a_responsive_fed"),
  matches("sr_28b_responsive_state"),
  matches("sr_28c_responsive_business"),

  matches("sr_27d_competent_ngo"),
  matches("sr_28d_responsive_ngo"),

  matches("sr_38_contact_admirable"),
  matches("sr_39_contact_good"),

  matches("sr_32_contact_useful"),
  matches("sr_33_contact_pleasant"),
  matches("sr_37_contact_foolish"),

  matches("sr_34_contact_cool"),
  matches("sr_35_contact_easy"),
  matches("sr_36_contact_exciting"))
p_missing <- unlist(lapply(OLRcompvarsmissing, function(x) sum(is.na(x))))/nrow(d_accept)
sort(p_missing[p_missing > 0], decreasing = TRUE)


```
#### Listwise deletion: we drop 40% of the data, from 1055 to 637 responses.
```{r eval=F, echo=F}
# Checking extent of missing data w/ listwise deletion
OLRdata <- d_accept %>% dplyr::select(
  matches("sr_24_past_contact"),
  matches("sr_25_future_contact"),
  
  matches("sr_19b_contacting_officials_spouse"),
  matches("sr_19c_contacting_officials_children"),
  
  matches("sr_19d_contacting_officials_otherfamily"),
  matches("sr_19e_contacting_officials_friends"),
  matches("sr_19f_contacting_officials_coworkers"),
  matches("sr_19g_contacting_officials_recpartners"),
  matches("sr_19h_contacting_officials_faithcommun"),

  matches("sr_20b_rolemodels_spouse"),
  matches("sr_20c_rolemodels_children"),

  matches("sr_20d_rolemodels_otherfamily"),
  matches("sr_20e_rolemodels_friends"),
  matches("sr_20f_rolemodels_coworkers"),
  matches("sr_20g_rolemodels_recpartners"),
  matches("sr_20h_rolemodels_faithcommun"),

  matches("sr_22b_expect_contact_spouse"),
  matches("sr_22c_expect_contact_children"),

  matches("sr_22d_expect_contact_otherfamily"),
  matches("sr_22e_expect_contact_friends"),
  matches("sr_22f_expect_contact_coworkers"),
  matches("sr_22g_expect_contact_recpartners"),
  matches("sr_22h_expect_contact_faithcommun"),

  matches("sr_23a_motivated_to_comply_parents"),
  matches("sr_23b_motivated_to_comply_spouse"),
  matches("sr_23c_motivated_to_comply_children"),

  matches("sr_23d_motivated_to_comply_otherfamily"),
  matches("sr_23e_motivated_to_comply_friends"),
  matches("sr_23f_motivated_to_comply_coworkers"),
  matches("sr_23g_motivated_to_comply_recpartners"),
  matches("sr_23h_motivated_to_comply_faithcommun"),

  matches("sr_16_hear_friends_talk"),
  matches("sr_17_hear_media"),
  matches("sr_18_hear_public_officials"),

  matches("sr_3a_importance_abortion"),
  matches("sr_8_importance_personally"),
  matches("sr_9_worried"),
  matches("sr_10_harm_you_personally"),

  matches("sr_29a_effective_fed"),
  matches("sr_29b_effective_state"),
  matches("sr_29c_effective_business"),
  matches("sr_29d_effective_ngo"),

  matches("sr_27a_competent_fed"),
  matches("sr_27b_competent_state"),
  matches("sr_27c_competent_business"),
  matches("sr_28a_responsive_fed"),
  matches("sr_28b_responsive_state"),
  matches("sr_28c_responsive_business"),

  matches("sr_27d_competent_ngo"),
  matches("sr_28d_responsive_ngo"),

  matches("sr_38_contact_admirable"),
  matches("sr_39_contact_good"),

  matches("sr_32_contact_useful"),
  matches("sr_33_contact_pleasant"),
  matches("sr_37_contact_foolish"),

  matches("sr_34_contact_cool"),
  matches("sr_35_contact_easy"),
  matches("sr_36_contact_exciting"),
  matches("sr_12a_actions_contacted_officials"),
  matches("race_present_dumvar"),
  matches("children_responded"),
  matches("gender"),
  matches("age"),
  -matches("age_range"),
  matches("sr_19a_contacting_officials__parents"),
  matches("sr_20a_rolemodels_parents"),
  matches("sr_22a_expect_contact_parents"),
  matches("sr_7_believe_about_climate_change"),
  matches("sr_11_harm_future_generations"),
  matches("sr_21a_effective_actions_contacting_officials"),
  matches("sr_30_easy_to_call"),
  matches("sr_31_able_to_call"),
  matches("sr_41a_right_to_modify"),
  matches("sr_41b_laws_of_nature"),
  matches("sr_41c_ingenuity"),
  matches("sr_41d_impotent"),
  matches("sr_41e_govt_do_more"),
  matches("sr_41f_equity"),
  matches("sr_56_marital_status"),
  matches("sr_61_education"),
  matches("sr_71_employment_status"),
  matches("sr_72_income"),
  matches("sr_78_political_affiliation"),
  matches("sr_79_political_leaning")
)

# We drop from 1055 to 520 respondents when using listwise deletion
OLR_complete_cases <- OLRdata[complete.cases(OLRdata), ]
dim(OLR_complete_cases)

```


#### Gender breakdown: 
```{r, eval=T, echo=F}
# EDA --IN PROGRESS--
# There are 1055 respondents in d_accept, but I can only find a sum of 1049 respondents across all gender options and I can't find a way to display those skips/"n/a"s???
d_accept %>% 
  summarize(female = sum(gender==1, na.rm = TRUE),
            femalepercent = sum(gender==1, na.rm = TRUE)/sum(gender, na.rm =TRUE),
            male = sum(gender==2, na.rm = TRUE),
            malepercent = sum(gender==2, na.rm = TRUE)/sum(gender, na.rm =TRUE),
            other = sum(gender==3, na.rm = TRUE),
            otherpercent = sum(gender==3, na.rm = TRUE)/sum(gender, na.rm =TRUE),
            noanswer = sum(gender==4, na.rm = TRUE),
            noanswerpercent = sum(gender==4, na.rm = TRUE)/sum(gender, na.rm =TRUE),
            total = sum((gender==1)+(gender==2)+(gender==3)+(gender==4), na.rm = TRUE))
```

#### Desc stats tables
```{r, eval=F, include=F, echo=F}
# Early viz and desc stats tables...in progress
for.stats <- d_accept %>% 
  dplyr::select(
    matches("year_born"),
    matches("age"),
    -matches("age_range"),
    -matches("rej_reason_garbage"))

basicStats(for.stats)

for.stats <- d_accept %>%
  dplyr::select(
    matches("sr_3[a-o]"),
    matches("sr_4[a-h]"))

basicStats(for.stats)
```


```{r, eval=F, include=F, echo=F}
# Checking for missing values across all variables. 
# Pulled this code randomly from internet. No idea how it works. 

cbind(
   lapply(
     lapply(d_accept, is.na)
     , sum)
   )

# ton of missing data on these questions:
# 40[a-r] 
# 14[a-j]
# 43-46
```

```{r, eval=F, include=F, echo=F}
# Age   

# Number of records w/ dependents, adult children, and no children
# 26.3% of resp did not answer question. 777 responses, 278 missing.
d_accept %>% 
  count(sr_57i_dependents >= 1)  # 274 resp w/ children <18
d_accept %>% 
  count(sr_57j_adultchildren >= 1)  # 393 resp w/ adult children
d_accept %>% 
  count(sr_57k_nochildren == 0)  # 110 resp w/ no children

# Change the obviously erroneous value of 99 dependents to NA
d_accept <- d_accept %>% 
    mutate(sr_57i_dependents = na_if(sr_57i_dependents, 99))  

# Create new variable for race to aid the listwise deletion. This race_present is a dummy var, 1 if respondent marked their race, 0 if the question was skipped. 
# With the way the race var was originally set up the listwise deletion would see the NAs in the other categories of race and delete the entry, even if one race had actually been chosen. 

# children_responded (1 category: 1==q answered, NA==question skipped)
d_accept <- d_accept %>%
  mutate(children_responded = ifelse(d_accept$sr_57i_dependents >= 1 | d_accept$sr_57j_adultchildren >= 1 | d_accept$sr_57k_nochildren==0,1,0))
  
# Check code
d_accept %>%
  dplyr::select(sr_57i_dependents, sr_57j_adultchildren, sr_57k_nochildren, children_responded) %>% 
  arrange(desc(sr_57i_dependents)) %>% 
  head(1000)

sum(d_accept$children_responded==1, na.rm=T)


# Percentage of missing data on race - 21% missing
totalvar <- count(respondents)

(totalvar - whitecount - othercount)/totalvar

# number of white respondents
whitecount <- sum(d_accept$sr_74_1_race_white==1, na.rm = T)
# number of other ethnicities
othercount <- sum(d_accept$sr_74_2_race_black==2 | d_accept$sr_74_3_race_hispanic==3 | d_accept$sr_74_4_race_native_american==4 | d_accept$sr_74_5_race_east_asian==5 | d_accept$sr_74_6_race_middle_eastern==6 | d_accept$sr_74_7_race_south_asian==7, na.rm = T)


# Create new variable for race to aid the listwise deletion. This race_present is a dummy var, 1 if respondent marked their race, 0 if the question was skipped. 
# With the way the race var was originally set up the listwise deletion would see the NAs in the other categories of race and delete the entry, even if one race had actually been chosen. 

# Race_present (1 category: 1==race chosen, NA==question skipped)
d_accept <- d_accept %>%
  mutate(race_present_dumvar = ifelse(d_accept$sr_74_1_race_white==1 | d_accept$sr_74_2_race_black==2 | d_accept$sr_74_3_race_hispanic==3 | d_accept$sr_74_4_race_native_american==4 | d_accept$sr_74_5_race_east_asian==5 | d_accept$sr_74_6_race_middle_eastern==6 | d_accept$sr_74_7_race_south_asian==7,1,0))
  
na_if(d_accept$race_present_dumvar, 0)

# Check code
d_accept %>%
  dplyr::select(sr_74_1_race_white, sr_74_2_race_black, sr_74_3_race_hispanic, sr_74_4_race_native_american, sr_74_5_race_east_asian, sr_74_6_race_middle_eastern, sr_74_7_race_south_asian, race_white_dumvar, race_present_dumvar) %>% 
  arrange(desc(race_white_dumvar)) %>% 
  head(1000)
```

```{r, eval=F, include=F, echo=F}
# EDA on dependent variables
mean(d_accept$sr_12a_actions_contacted_officials, na.rm=TRUE)
sd(d_accept$sr_12a_actions_contacted_officials, na.rm=TRUE)

# intention
mean(d_accept$sr_13a_takeactions_contact_officials, na.rm=TRUE)
sd(d_accept$sr_13a_takeactions_contact_officials, na.rm=TRUE)
```

# Principal Components Analysis
$$\\[.05in]$$
### Dynamic Norms
*"Do you think that over the PAST/NEXT 12 months the percentage of adults in the United States who contacted elected officials to urge them to take action to reduce global warming is..."*   

One factor solution:   
1. Two-item factor consisting of the two dynamic norms questions (changes in the number of ppl contacting reps in the past and future)

```{r eval=F, include=F}
# Visualize variables
# *** Need to address errors in this visualization code ***

ggscatter(d_accept, x = "sr_24_past_contact", y = "sr_25_future_contact", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Test x", ylab = "Test Y")

shapiro.test(d_accept$sr_24_past_contact)
ggqqplot(d_accept$sr_24_past_contact, ylab = "past contact")

shapiro.test(d_accept$sr_25_future_contact)
ggqqplot(d_accept$sr_25_future_contact, ylab = "future contact")
```

```{r, eval=T, echo=F, warning=F}
res <- cor.test(d_accept$sr_24_past_contact,d_accept$sr_25_future_contact, method = "spearman")
print(res)

#mean(d_accept$sr_24_past_contact, na.rm=TRUE)
#sd(d_accept$sr_24_past_contact, na.rm=TRUE)

#mean(d_accept$sr_25_future_contact, na.rm=TRUE)
#sd(d_accept$sr_25_future_contact, na.rm=TRUE)
```
Correlation test of the two dynamic norms items shows strong positive correlation, with Spearman's rho of `r res$estimate` and p-value of `r res$p.value`.

$$\\[.05in]$$

### Descriptive Norms (contact)
*"To what extent do you think that the following people ARE CONTACTING (writing letters, emailing, or calling) their elected representatives in Congress to urge action on reducing climate change?"*

Three factor solution (70% cumulative variance (hereafter: cv))   
1. 1-item variable: Parents   
2. 2-item composite variable: Spouse, Children   
3. Multi-item composite variable: Non-immediate family

```{r, eval=T, echo=F}
d_pca_descriptivecontactnorms <- d_accept %>% 
  dplyr::select(
    matches("sr_19a"),
    matches("sr_19b"),
    matches("sr_19c"),
    matches("sr_19d"),
    matches("sr_19e"),
    matches("sr_19f"),
    matches("sr_19g"),
    matches("sr_19h"))
    
fa.parallel(d_pca_descriptivecontactnorms, fm='minres', fa='fa')
pca1 <- fa(d_pca_descriptivecontactnorms, nfactors = 4, rotate = "Varimax", fm="minres") 
print(pca1)
print(pca1$loadings,cutoff = 0.3)
```

#### Descriptive Norms (contact) - 1st factor (Parents) - desc stats
```{r, eval=T, echo=T}
mean(d_accept$sr_19a_contacting_officials__parents, na.rm=TRUE)
sd(d_accept$sr_19a_contacting_officials__parents, na.rm=TRUE)

summary(d_pca_descriptivecontactnorms)
sapply(d_pca_descriptivecontactnorms, sd, na.rm=TRUE)
```

#### Descriptive Norms (contact) - 2nd factor (Spouse & Children) - Correlation & desc stats
```{r, eval=T, echo=F}
res <- cor.test(d_accept$sr_19b_contacting_officials_spouse,d_accept$sr_19c_contacting_officials_children, method = "spearman", exact=FALSE)
print(res)

# mean(d_accept$sr_19b_contacting_officials_spouse, na.rm=TRUE)
# sd(d_accept$sr_19b_contacting_officials_spouse, na.rm=TRUE)

# mean(d_accept$sr_19c_contacting_officials_children, na.rm=TRUE)
# sd(d_accept$sr_19c_contacting_officials_children, na.rm=TRUE)
```
Correlation test of the two descriptive norms items for Spouse and Children, showing moderate positive correlation. Spearman's rho is `r res$estimate` with a p-value of `r res$p.value`.

#### Descriptive Norms (contact) - 3rd factor (Non-immediate family) - Cronbach Alpha
```{r, eval=T, echo=F}
d_pca_descriptivecontactnormsnonfamily <- d_accept %>% 
  dplyr::select(
    matches("sr_19d"),
    matches("sr_19e"),
    matches("sr_19f"),
    matches("sr_19g"),
    matches("sr_19h"))

psych::alpha(d_pca_descriptivecontactnormsnonfamily, use ="pairwise", na.rm = TRUE) 
```

$$\\[.05in]$$

### Descriptive Norms (role models)
*"How likely are you to consider each of these groups as behavioral role models?"*

Scree plot suggests four factors (78% cumulative var), but three factor solution makes the most sense.   
Three factor solution (71% cv):   
1. 1-item variable: Parents   
2. 2-item composite variable: Spouse, Children   
3. Multi-item composite variable: Non-immediate family

```{r eval=TRUE, echo=F}
d_pca_descriptiverolemodelnorms <- d_accept %>% 
  dplyr::select(
    matches("sr_20a"),
    matches("sr_20b"),
    matches("sr_20c"),
    matches("sr_20d"),
    matches("sr_20e"),
    matches("sr_20f"),
    matches("sr_20g"),
    matches("sr_20h"))
    
fa.parallel(d_pca_descriptiverolemodelnorms, fm='minres', fa='fa')
pca1 <- fa(d_pca_descriptiverolemodelnorms, nfactors = 4, rotate = "Varimax", fm="minres") 
print(pca1)
print(pca1$loadings,cutoff = 0.3) 
```

#### Descriptive Norms (role models) - 1st factor (Parents) - Descriptive stats
```{r, eval=T, echo=F}
mean(d_accept$sr_20a_rolemodels_parents, na.rm=TRUE)
sd(d_accept$sr_20a_rolemodels_parents, na.rm=TRUE)
```


#### Descriptive Norms (role models) - 2nd factor (Spouse & Children) - Correlation
```{r, eval=T, echo=F}
res <- cor.test(d_accept$sr_20b_rolemodels_spouse,d_accept$sr_20c_rolemodels_children, method = "spearman", exact=FALSE)
print(res)

mean(d_accept$sr_20b_rolemodels_spouse, na.rm=TRUE)
sd(d_accept$sr_20b_rolemodels_spouse, na.rm=TRUE)

mean(d_accept$sr_20c_rolemodels_children, na.rm=TRUE)
sd(d_accept$sr_20c_rolemodels_children, na.rm=TRUE)
```
Correlation test of the two descriptive norms items for Spouse and Children, showing moderate positive correlation. Spearman's rho is `r res$estimate` with a p-value of `r res$p.value`.

#### Descriptive Norms (role models) - 3rd factor (Non-immediate family) - Cronbach Alpha
```{r, eval=T, echo=F}
d_pca_descriptiverolemodelnormsnonfamily <- d_accept %>% 
  dplyr::select(
    matches("sr_20d"),
    matches("sr_20e"),
    matches("sr_20f"),
    matches("sr_20g"),
    matches("sr_20h"))

psych::alpha(d_pca_descriptiverolemodelnormsnonfamily, use ="pairwise", na.rm = TRUE) 

summary(d_pca_descriptivecontactnormsnonfamily)
sapply(d_pca_descriptivecontactnormsnonfamily, sd, na.rm=TRUE)
```

$$\\[.05in]$$

### Injunctive Norms (contact) 
*"To what extent do you think that the following people EXPECT YOU to contact (writing letters, emailing, or calling) your elected representatives to urge action on reducing climate change?"*

Scree plot suggests four factors (78% cv) but three (73% cv) makes the most sense.     
Three-factor solution:   
1. 1-item variable: Parents   
2. 2-item composite variable: Spouse, Children   
3. Multi-item composite variable: Non-immediate family

```{r, eval=T, echo=F}
d_pca_injunctivecontactnorms <- d_accept %>% 
  dplyr::select(
    matches("sr_22a"),
    matches("sr_22b"),
    matches("sr_22c"),
    matches("sr_22d"),
    matches("sr_22e"),
    matches("sr_22f"),
    matches("sr_22g"),
    matches("sr_22h"))

fa.parallel(d_pca_injunctivecontactnorms, fm='minres', fa='fa')
pca1 <- fa(d_pca_injunctivecontactnorms, nfactors = 4, rotate = "Varimax", fm="minres") 
print(pca1)
print(pca1$loadings,cutoff = 0.3)

summary(d_pca_injunctivecontactnorms)
sapply(d_pca_injunctivecontactnorms, sd, na.rm=TRUE)
```

#### Injunctive Norms (contact) - 2nd factor (Spouse & Children) - Correlation
```{r, eval=T, echo=F}
res <- cor.test(d_accept$sr_22b_expect_contact_spouse,d_accept$sr_22c_expect_contact_children, method = "spearman", exact=FALSE)
print(res)
```
Correlation test of the two descriptive norms items for Spouse and Children, showing moderate positive correlation. Spearman's rho is `r res$estimate` with a p-value of `r res$p.value`.

#### Injunctive Norms (contact) - 3rd factor (Non-family) - Cronbach Alpha
```{r, eval=T, echo=F}
d_pca_injunctivecontactnormsnonfamily <- d_accept %>% 
  dplyr::select(
    matches("sr_22d"),
    matches("sr_22e"),
    matches("sr_22f"),
    matches("sr_22g"),
    matches("sr_22h"))

psych::alpha(d_pca_injunctivecontactnormsnonfamily, use ="pairwise", na.rm = TRUE) 
```
$$\\[.05in]$$

### Injunctive Norms (compliance)
*"How motivated are you to comply with the expectations of each of these people?"*

Two factor solution (70% cv)    
1. Multi-item composite variable: Parents, Spouse, Children   
2. Multi-item composite variable: Otherfam, Friends, Cowork, Recpartners, Faith

```{r, eval=T, echo=F}
d_pca_injunctivecompliance <- d_accept %>% 
  dplyr::select(
    matches("sr_23a"),
    matches("sr_23b"),
    matches("sr_23c"),
    matches("sr_23d"),
    matches("sr_23e"),
    matches("sr_23f"),
    matches("sr_23g"),
    matches("sr_23h"))

fa.parallel(d_pca_injunctivecompliance, fm='minres', fa='fa')
pca1 <- fa(d_pca_injunctivecompliance, nfactors = 2, rotate = "Varimax", fm="minres") 
print(pca1)
print(pca1$loadings,cutoff = 0.3)

summary(d_pca_injunctivecompliance)
sapply(d_pca_injunctivecompliance, sd, na.rm=TRUE)
```

#### Injunctive Norms (compliance) - 1st factor (Immediate Family) - Cronbach Alpha
```{r, eval=T, echo=F}
d_pca_injunctivecompliancefamily <- d_accept %>% 
  dplyr::select(
    matches("sr_23a"),
    matches("sr_23b"),
    matches("sr_23c"))

psych::alpha(d_pca_injunctivecompliancefamily, use ="pairwise", na.rm = TRUE) 
```

#### Injunctive Norms (compliance) - 2nd factor (Non-family) - Cronbach Alpha
```{r, eval=T, echo=F}
d_pca_injunctivecompliancenonfamily <- d_accept %>% 
  dplyr::select(
    matches("sr_23d"),
    matches("sr_23e"),
    matches("sr_23f"),
    matches("sr_23g"),
    matches("sr_23h"))

psych::alpha(d_pca_injunctivecompliancenonfamily, use ="pairwise", na.rm = TRUE) 
```

$$\\[.05in]$$

### CIM - Benefits
*"How often do you hear ____ talk about the importance of reducing climate change?"*   
*[your friends, family, and coworkers]*   
*[public figures whom you respect]*   
*[about the importance of reducing climate change in the media? (TV, movies, radio, newspapers/news websites, magazines, etc.)]*

One-factor solution:   
1. Multi-item composite variable: F/Fam/Cowork, Public Figures, Media

```{r, eval=T, echo=F}
d_pca_CIMbenefits <- d_accept %>% 
  dplyr::select(
    matches("sr_16"),
    matches("sr_17"),
    matches("sr_18"))

fa.parallel(d_pca_CIMbenefits, fm='minres', fa='fa')
pca1 <- fa(d_pca_CIMbenefits, nfactors = 1, rotate = "Varimax", fm="minres") 
print(pca1)
print(pca1$loadings,cutoff = 0.3)
```

#### CIM - Benefits - Cronbach Alpha
```{r, eval=T, echo=F}
psych::alpha(d_pca_CIMbenefits, use ="pairwise", na.rm = TRUE) 
```

$$\\[.05in]$$

### CIM - Perceived Risk
*"How important is each of the following issues to you today?"*   
*"How important is the issue of climate change to you personally?"*   
*"How worried are you about climate change?"*   
*"How much do you think climate change will harm you personally?"*   
*"How much do you think climate change will harm future generations of people?"*

NOTE - removing #7 for now until I understand how to properly account for it. 

Three-factor solution   
1. Multi-item composite variable: CC importance as an issue, CC personal importance, CC worry, belief of personal harm from CC    
2. 1-item variable: anthropocentric CC belief
3. 1-item variable: belief of harm to future generations from CC

```{r, eval=T, echo=F}
d_pca_CIMperceivedrisk <- d_accept %>% 
  dplyr::select(
    matches("sr_3b_importance_climatechange"),
    matches("sr_8_importance_personally"),
    matches("sr_9_worried"),
    matches("sr_10_harm_you_personally"),
    matches("sr_11_harm_future_generations"))

fa.parallel(d_pca_CIMperceivedrisk, fm='minres', fa='fa')
pca1 <- fa(d_pca_CIMperceivedrisk, nfactors = 2, rotate = "Varimax", fm="minres") 
print(pca1)
print(pca1$loadings,cutoff = 0.3)
```

#### CIM - Perceived Risk - 1st factor (Personal) - Cronbach Alpha
```{r, eval=T, echo=F}
d_pca_CIMperceivedriskpersonal <- d_accept %>% 
  dplyr::select(
    matches("sr_3b_importance_climatechange"),
    matches("sr_8_importance_personally"),
    matches("sr_9_worried"),
    matches("sr_10_harm_you_personally"))

psych::alpha(d_pca_CIMperceivedriskpersonal, use ="pairwise", na.rm = TRUE) 
```

#### CIM - Perceived Risk - Descriptive stats on single-item variables
```{r, eval=T, echo=T}

mean(d_accept$sr_11_harm_future_generations, na.rm=TRUE)
sd(d_accept$sr_11_harm_future_generations, na.rm=TRUE)

mean(d_accept$sr_7_believe_about_climate_change, na.rm=TRUE)
sd(d_accept$sr_7_believe_about_climate_change, na.rm=TRUE)

```
$$\\[.05in]$$

### Efficacy
*"Below is a list of actions that individuals could take to reduce climate change. If YOU took these actions, how effective would each be for reducing climate change?"*   
*"Below are some public and private organizations who make decisions that have an impact on climate change. In general, how COMPETENT is each in addressing climate change?"*   
*"In general, how RESPONSIVE is each in addressing climate change?"*   
*"How much do you agree that each type of organization is generally IN A POSITION TO EFFECTIVELY reduce climate change?"* 

Three-factor solution:   
1. 1-item variable: 21a: Is contacting elected reps an effective action?   
2. Multi-item composite variable: All types (fed, state, business, ngo) are in a position to effect change   
3. Multi-item composite variable: The competency and responsiveness of fed, state, and business   
4. 2-item composite variable: The competency and responsiveness of ngo only

```{r, eval=T, echo=F}
d_pca_efficacysecond <- d_accept %>% 
  dplyr::select(
    matches("sr_27[a-d]"),
    matches("sr_28[a-d]"),
    matches("sr_29[a-d]"))

fa.parallel(d_pca_efficacysecond, fm='minres', fa='fa')
pca1 <- fa(d_pca_efficacysecond, nfactors = 3, rotate = "Varimax", fm="minres") 
print(pca1)
print(pca1$loadings,cutoff = 0.3)
```

#### Efficacy - 1st variable (contacting elected officials an effective action?)
```{r, eval=T, echo=F}
mean(d_accept$sr_21a_effective_actions_contacting_officials, na.rm=TRUE)
sd(d_accept$sr_21a_effective_actions_contacting_officials, na.rm=TRUE)
```

#### Efficacy - 2nd Factor (All types' ability to effect change) - Cronbach Alpha 
```{r, eval=T, echo=F}
d_pca_efficacyeffectchangesecond <- d_accept %>% 
  dplyr::select(
    matches("sr_29[a-d]"))

psych::alpha(d_pca_efficacyeffectchangesecond, use ="pairwise", na.rm = TRUE) 
```

#### Efficacy - 3rd Factor (Competency & Responsiveness of Fed, State, and Business) - Cronbach Alpha 
```{r, eval=T, echo=F}
d_pca_efficacycompetencyresponsivesecond <- d_accept %>% 
  dplyr::select(
    matches("sr_27[a-c]"),
    matches("sr_28[a-c]"))

psych::alpha(d_pca_efficacycompetencyresponsivesecond, use ="pairwise", na.rm = TRUE) 
```

#### Efficacy - 4th Factor (Competency & Responsiveness of NGO) - Correlation 
```{r, eval=T, echo=F}
res <- cor.test(d_accept$sr_27d_competent_ngo,d_accept$sr_28d_responsive_ngo, method = "spearman", exact=FALSE)
print(res)

mean(d_accept$sr_27d_competent_ngo, na.rm=TRUE)
sd(d_accept$sr_27d_competent_ngo, na.rm=TRUE)

mean(d_accept$sr_28d_responsive_ngo, na.rm=TRUE)
sd(d_accept$sr_28d_responsive_ngo, na.rm=TRUE)
```
Correlation test of the competency and responsiveness scores for NGOs shows moderate positive correlation. Spearman's rho is `r res$estimate` with a p-value of `r res$p.value`.  

$$\\[.05in]$$

### TPB Behavioral Attitude (CHECK CODE - ERRORS?)
*"For me, contacting (writing letters, emailing, phoning my elected representatives in Congress to urge action on climate change on a regular basis during the next year would be …"*

Three-factor solution:   
1. Multi-item composite variable: cool/uncool, admirable/shameful, good/bad, exciting/boring   
2. Multi-item composite variable: useful/useless, pleasant/intimidating, sensible/foolish  
3. 1-item variable: easy/awkward   

```{r, eval=F, echo=F, include=F}
d_pca_behavioralattitude <- d_accept %>% 
    dplyr::select(-"sr_32_contact_useful_reversed") %>% 
    dplyr::select(-"sr_33_contact_pleasant_reversed") %>% 
    dplyr::select(-"sr_37_contact_foolish_reversed") %>% 
  dplyr::select(
    matches("sr_32"),
    matches("sr_33"),
    matches("sr_34"),
    matches("sr_35"),
    matches("sr_36"),
    matches("sr_37"),
    matches("sr_38"),
    matches("sr_39"))


fa.parallel(d_pca_behavioralattitude, fm='minres', fa='fa')
pca1 <- fa(d_pca_behavioralattitude, nfactors = 3, rotate = "Varimax", fm="minres") 
print(pca1)
print(pca1$loadings,cutoff = 0.3)
```

```{r, eval=T, echo=F}
d_accept <- d_accept %>% 
  mutate(sr_32_contact_useful_reversed = car::recode(sr_32_contact_useful, "1=6 ; 2=5 ; 3=4 ; 4=3 ; 5=2 ; 6=1")) 

d_accept <- d_accept %>% 
  mutate(sr_33_contact_pleasant_reversed = car::recode(sr_33_contact_pleasant, "1=6 ; 2=5 ; 3=4 ; 4=3 ; 5=2 ; 6=1"))

d_accept <- d_accept %>%
  mutate(sr_37_contact_foolish_reversed = car::recode(sr_37_contact_foolish, "1=6 ; 2=5 ; 3=4 ; 4=3 ; 5=2 ; 6=1"))

ba2 <- d_accept %>% 
  dplyr::select(
    matches("sr_32_contact_useful_reversed"),
    matches("sr_33_contact_pleasant_reversed"),
    matches("sr_34"),
    matches("sr_35"),
    matches("sr_36"),
    matches("sr_37_contact_foolish_reversed"),
    matches("sr_38"),
    matches("sr_39"))


fa.parallel(ba2, fm='minres', fa='fa')
pca1 <- fa(ba2, nfactors = 3, rotate = "Varimax", fm="minres") 
print(pca1)
print(pca1$loadings,cutoff = 0.3)
```

#### TPB Behavioral Attitude - 1st factor - Correlation
```{r, eval=T, echo=F}
res <- cor.test(d_accept$sr_38_contact_admirable,d_accept$sr_39_contact_good, method = "spearman")
print(res)
```
The two measures of perceived behavioral control show a moderate positive relationship, just barely under the .65 rule of thumb. Spearman's rho is `r res$estimate` with a p-value of `r res$p.value`.   


#### TPB Behavioral Attitude - 2nd factor - Cronbach Alpha
```{r, eval=T, echo=F}
d_pca_behavioralattitude2 <- d_accept %>% 
  dplyr::select(
    matches("sr_32_contact_useful_reversed"),
    matches("sr_33_contact_pleasant_reversed"),
    matches("sr_37_contact_foolish_reversed"))

psych::alpha(d_pca_behavioralattitude2, use ="pairwise", na.rm = TRUE) 
```

#### TPB Behavioral Attitude - 3rd factor - Cronbach Alpha
```{r, eval=T, echo=F}
d_pca_behavioralattitude3 <- d_accept %>% 
  dplyr::select(
    matches("sr_34"),
    matches("sr_35"),
    matches("sr_36"))

psych::alpha(d_pca_behavioralattitude3, use ="pairwise", na.rm = TRUE) 
```

$$\\[.05in]$$
#### Perceived Behavioral Control - correlation
```{r, eval=T, echo=F, warning=F}
mean(d_accept$sr_35_contact_easy, na.rm=TRUE)
sd(d_accept$sr_35_contact_easy, na.rm=TRUE)
```

```{r, eval=T, echo=F, warning=F}
res <- cor.test(d_accept$sr_30_easy_to_call,d_accept$sr_31_able_to_call, method = "spearman")
print(res)

#mean(d_accept$sr_30_easy_to_call, na.rm=TRUE)
#sd(d_accept$sr_30_easy_to_call, na.rm=TRUE)

#mean(d_accept$sr_31_able_to_call, na.rm=TRUE)
#sd(d_accept$sr_31_able_to_call, na.rm=TRUE)
```
The two measures of perceived behavioral control show a moderate positive relationship, just barely under the .65 rule of thumb. Spearman's rho is `r res$estimate` with a p-value of `r res$p.value`. This is not a strong enough correlation to justify a composite variable of the two items, so they will stay separate.

$$\\[.05in]$$

### Worldviews
We decided these will be kept as-is.

```{r, eval=T, echo=F}
d_worldviews <- d_accept %>% 
  dplyr::select(
    matches("sr_41a"),
    matches("sr_41b"),
    matches("sr_41c"),
    matches("sr_41d"),
    matches("sr_41e"),
    matches("sr_41f"))

summary(d_worldviews)
sapply(d_worldviews, sd, na.rm=TRUE)
```
$$\\[.05in]$$


# Creating PCA variables for regression
#### note: leaving this out of the markup file unless you'd like to review the variable creation code
```{r, eval=T, include=F}
# Dynamic, descriptive, and injunctive norms
d_accept <- d_accept %>% 
  mutate(
    descdynamicnorms_comp = rowMeans(subset(d_accept, select = c(sr_24_past_contact, sr_25_future_contact)), na.rm = T),
    desccontactnorms_fam_comp = rowMeans(subset(d_accept, select = c(sr_19b_contacting_officials_spouse, sr_19c_contacting_officials_children)), na.rm = T),
    desccontactnorms_nf_comp = rowMeans(subset(d_accept, select = c(sr_19d_contacting_officials_otherfamily, sr_19e_contacting_officials_friends, sr_19f_contacting_officials_coworkers, sr_19g_contacting_officials_recpartners, sr_19h_contacting_officials_faithcommun)), na.rm=T),
    descrolemodelnorms_fam_comp = rowMeans(subset(d_accept, select = c(sr_20b_rolemodels_spouse, sr_20c_rolemodels_children)), na.rm = T),
    descrolemodelnorms_nf_comp = rowMeans(subset(d_accept, select = c(sr_20d_rolemodels_otherfamily, sr_20e_rolemodels_friends, sr_20f_rolemodels_coworkers, sr_20g_rolemodels_recpartners, sr_20h_rolemodels_faithcommun)), na.rm=T),
    injunctcontactnorms_fam_comp = rowMeans(subset(d_accept, select = c(sr_22b_expect_contact_spouse, sr_22c_expect_contact_children)), na.rm = T),
    injunctcontactnorms_nf_comp = rowMeans(subset(d_accept, select = c(sr_22d_expect_contact_otherfamily, sr_22e_expect_contact_friends, sr_22f_expect_contact_coworkers, sr_22g_expect_contact_recpartners, sr_22h_expect_contact_faithcommun)), na.rm=T),
    injunctmotivation_fam_comp = rowMeans(subset(d_accept, select = c(sr_23a_motivated_to_comply_parents, sr_23b_motivated_to_comply_spouse,sr_23c_motivated_to_comply_children)), na.rm = T),
    injunctmotivation_nf_comp = rowMeans(subset(d_accept, select = c(sr_23d_motivated_to_comply_otherfamily, sr_23e_motivated_to_comply_friends, sr_23f_motivated_to_comply_coworkers, sr_23g_motivated_to_comply_recpartners, sr_23h_motivated_to_comply_faithcommun)), na.rm = T),
      )

# CIM - Benefits
d_accept <- d_accept %>% 
  mutate(
    cimbenefits_comp = rowMeans(subset(d_accept, select = c(sr_16_hear_friends_talk, sr_17_hear_media, sr_18_hear_public_officials)), na.rm = T))

# CIM - Perceived Risk
d_accept <- d_accept %>% 
  mutate(
    cimperceivedrisk_comp = rowMeans(subset(d_accept, select = c(sr_3a_importance_abortion, sr_8_importance_personally, sr_9_worried, sr_10_harm_you_personally)), na.rm = T))

# Efficacy
d_accept <- d_accept %>% 
  mutate(
    efficacy_effectiveness_comp = rowMeans(subset(d_accept, select = c(sr_29a_effective_fed, sr_29b_effective_state, sr_29c_effective_business, sr_29d_effective_ngo)), na.rm = T),
    efficacy_fedstatebusiness_competresp_comp = rowMeans(subset(d_accept, select = c(sr_27a_competent_fed, sr_27b_competent_state, sr_27c_competent_business, sr_28a_responsive_fed, sr_28b_responsive_state, sr_28c_responsive_business)), na.rm = T),
    efficacy_ngo_competresp_comp = rowMeans(subset(d_accept, select = c(sr_27d_competent_ngo, sr_28d_responsive_ngo)), na.rm = T)
    )

# TPB - Behavioral Attitude
d_accept <- d_accept %>% 
  mutate(
    behatt_admirablegood_comp = rowMeans(subset(d_accept, select = c(sr_38_contact_admirable, sr_39_contact_good)), na.rm = T),
    behatt_usefulpleasantsensible_comp = rowMeans(subset(d_accept, select = c(sr_32_contact_useful_reversed, sr_33_contact_pleasant_reversed, sr_37_contact_foolish_reversed)), na.rm = T),
    behatt_coolexcitingeasy_comp = rowMeans(subset(d_accept, select = c(sr_34_contact_cool, sr_35_contact_easy, sr_36_contact_exciting)), na.rm = T)
    )

# test to make sure variable-creation code is working
d_accept %>% 
  dplyr::select(sr_32_contact_useful_reversed, sr_33_contact_pleasant_reversed, sr_37_contact_foolish_reversed, behatt_usefulpleasantsensible_comp)
```

```{r, eval=F, echo=F}
mean(d_accept$descdynamicnorms_comp, na.rm=T)
sd(d_accept$descdynamicnorms_comp, na.rm=T)

mean(d_accept$desccontactnorms_fam_comp, na.rm=T)
sd(d_accept$desccontactnorms_fam_comp, na.rm=T)

mean(d_accept$desccontactnorms_nf_comp, na.rm=T)
sd(d_accept$desccontactnorms_nf_comp, na.rm=T)

mean(d_accept$descrolemodelnorms_fam_comp, na.rm=T)
sd(d_accept$descrolemodelnorms_fam_comp, na.rm=T)

mean(d_accept$descrolemodelnorms_nf_comp, na.rm=T)
sd(d_accept$descrolemodelnorms_nf_comp, na.rm=T)

mean(d_accept$injunctcontactnorms_fam_comp, na.rm=T)
sd(d_accept$injunctcontactnorms_fam_comp, na.rm=T)

mean(d_accept$injunctcontactnorms_nf_comp, na.rm=T)
sd(d_accept$injunctcontactnorms_nf_comp, na.rm=T)

mean(d_accept$injunctmotivation_fam_comp, na.rm=T)
sd(d_accept$injunctmotivation_fam_comp, na.rm=T)

mean(d_accept$injunctmotivation_nf_comp, na.rm=T)
sd(d_accept$injunctmotivation_nf_comp, na.rm=T)

mean(d_accept$cimbenefits_comp, na.rm=T)
sd(d_accept$cimbenefits_comp, na.rm=T)

mean(d_accept$cimperceivedrisk_comp, na.rm=T)
sd(d_accept$cimperceivedrisk_comp, na.rm=T)

mean(d_accept$efficacy_effectiveness_comp, na.rm=T)
sd(d_accept$efficacy_effectiveness_comp, na.rm=T)

mean(d_accept$efficacy_fedstatebusiness_competresp_comp, na.rm=T)
sd(d_accept$efficacy_fedstatebusiness_competresp_comp, na.rm=T)

mean(d_accept$efficacy_ngo_competresp_comp, na.rm=T)
sd(d_accept$efficacy_ngo_competresp_comp, na.rm=T)

mean(d_accept$behatt_admirablegood_comp, na.rm=T)
sd(d_accept$behatt_admirablegood_comp, na.rm=T)

mean(d_accept$behatt_usefulpleasantsensible_comp, na.rm=T)
sd(d_accept$behatt_usefulpleasantsensible_comp, na.rm=T)

mean(d_accept$behatt_coolexcitingeasy_comp, na.rm=T)
sd(d_accept$behatt_coolexcitingeasy_comp, na.rm=T)
```
$$\\[.05in]$$

# Creating dummy categorical variables
#### note: leaving this out of the markup file unless you'd like to review the variable creation code
```{r, eval=T, include=F}
# Gender (3 categories: Female, male, other, prefer not to say. Ref: Female)
d_accept <- dummy_cols(d_accept, select_columns = 'gender')

d_accept <- d_accept %>% 
  rename(gender_female = gender_1,
         gender_male = gender_2,
         gender_other = gender_3,
         gender_prefernottosay = gender_4)

d_accept %>% 
  dplyr::select(
    starts_with("gender")
  )

# Marital Status (3 categories: single, married/partner, divorced/separated, widowed. Ref: Single)
d_accept <- dummy_cols(d_accept, select_columns = "sr_56_marital_status")

d_accept <- d_accept %>% 
  rename(sr_56_marital_status_single = sr_56_marital_status_1,
         sr_56_marital_status_marriedpartner = sr_56_marital_status_2,
         sr_56_marital_status_divorcedseparated = sr_56_marital_status_3,
         sr_56_marital_status_widowed = sr_56_marital_status_4)

d_accept %>% 
  dplyr::select(
    starts_with("sr_56_marital_status")
  )

# Education level (5 categories: some high school, high school grad or equiv, some college, Assoc deg, Bachelor deg, Grad/prof deg. Ref: Some high school)
d_accept <- dummy_cols(d_accept, select_columns = "sr_61_education")

d_accept <- d_accept %>% 
  rename(sr_61_education_somehighschool = sr_61_education_1,
         sr_61_education_highschooldegree = sr_61_education_2,
         sr_61_education_somecollege = sr_61_education_3,
         sr_61_education_associatedegree = sr_61_education_4,
         sr_61_education_bachelordegree = sr_61_education_5,
         sr_61_education_gradorprofdegree = sr_61_education_6)

d_accept %>% 
  dplyr::select(
    starts_with("sr_61_education")
  )

# Type of work (5 categories: fulltime work, parttime work, homemaker, retired/semiretired, student, unemployed. Ref: Fulltime work)
d_accept <- dummy_cols(d_accept, select_columns = "sr_71_employment_status")

d_accept <- d_accept %>% 
  rename(sr_71_employment_status_workfulltime = sr_71_employment_status_1,
         sr_71_employment_status_workparttime = sr_71_employment_status_2,
         sr_71_employment_status_homemaker = sr_71_employment_status_3,
         sr_71_employment_status_retired = sr_71_employment_status_4,
         sr_71_employment_status_student = sr_71_employment_status_5,
         sr_71_employment_status_unemployed = sr_71_employment_status_6)

d_accept %>% 
  dplyr::select(
    starts_with("sr_71_employment_status")
  )

# Income level (8 categories: under25k, 25-50, 50-75, 75-100, 100-150. 150-200, 200-250, 250+, prefer not to say. Ref: under25k)
d_accept <- dummy_cols(d_accept, select_columns = "sr_72_income")

d_accept <- d_accept %>% 
  rename(sr_72_income_under25k = sr_72_income_1,
         sr_72_income_25to49k = sr_72_income_2,
         sr_72_income_50to74k = sr_72_income_3,
         sr_72_income_75to99k = sr_72_income_4,
         sr_72_income_100to149k = sr_72_income_5,
         sr_72_income_150to199k = sr_72_income_6,
         sr_72_income_200to249k = sr_72_income_7,
         sr_72_income_over250k = sr_72_income_8,
         sr_72_income_prefernottoanswer = sr_72_income_9)

d_accept %>% 
  dplyr::select(
    starts_with("sr_72_income")
  )

# Race (1 category: white, any other. Ref: white) # race_white_dumvar
d_accept <- d_accept %>%
  mutate(race_white_dumvar = ifelse(d_accept$sr_74_1_race_white==1 & is.na(d_accept$sr_74_2_race_black) & is.na(d_accept$sr_74_3_race_hispanic) & is.na(d_accept$sr_74_4_race_native_american) & is.na(d_accept$sr_74_5_race_east_asian) & is.na(d_accept$sr_74_6_race_middle_eastern) & is.na(d_accept$sr_74_7_race_south_asian),1,0))
  
# CHeck code
d_accept %>%
  dplyr::select(sr_74_1_race_white, sr_74_2_race_black, sr_74_3_race_hispanic, sr_74_4_race_native_american, sr_74_5_race_east_asian, sr_74_6_race_middle_eastern, sr_74_7_race_south_asian, race_white_dumvar) %>% 
  arrange(desc(race_white_dumvar)) %>% 
  head(700)
  
# Political affiliation (5 categories: Dem, Rep, Independent, Green party, Libertarian, No party. Ref: Dem)
d_accept <- dummy_cols(d_accept, select_columns = "sr_78_political_affiliation")

d_accept <- d_accept %>% 
  rename(sr_78_political_affiliation_Dem = sr_78_political_affiliation_1,
         sr_78_political_affiliation_Rep = sr_78_political_affiliation_2,
         sr_78_political_affiliation_Ind = sr_78_political_affiliation_3,
         sr_78_political_affiliation_Green = sr_78_political_affiliation_4,
         sr_78_political_affiliation_Libertarian = sr_78_political_affiliation_5,
         sr_78_political_affiliation_NoParty = sr_78_political_affiliation_6)

# Check code
d_accept %>% 
  dplyr::select(
    starts_with("sr_78_political_affiliation")
  )

# Ideology (4 categories: very lib, somewhat lib, moderate, somewhat conservative, very conservative. Ref: Very liberal)
d_accept <- dummy_cols(d_accept, select_columns = "sr_79_political_leaning")

d_accept <- d_accept %>% 
  rename(sr_79_political_leaning_VeryLib = sr_79_political_leaning_1,
         sr_79_political_leaning_SomeLib = sr_79_political_leaning_2,
         sr_79_political_leaning_Moderate = sr_79_political_leaning_3,
         sr_79_political_leaning_SomeConservative = sr_79_political_leaning_4,
         sr_79_political_leaning_VeryConservative = sr_79_political_leaning_5)

# Check code
d_accept %>% 
  dplyr::select(
    starts_with("sr_79_political_leaning")
  )

```

$$\\[.05in]$$
# Ordinal logistic regression model
```{r, eval=T, include=T}
library(MASS)

# Convert RV (12a) past contact to a factor and assign labels
d_accept$sr_12a_actions_contacted_officials_factor <- factor(d_accept$sr_12a_actions_contacted_officials, ordered=TRUE, levels <- c(1, 2, 3))

d_accept$sr_12a_actions_contacted_officials_factor <- recode_factor(d_accept$sr_12a_actions_contacted_officials_factor, "1"="NoContact", "2"="Once", "3"="MoreOnce")

d_accept %>%
  dplyr::select(sr_12a_actions_contacted_officials_factor, sr_12a_actions_contacted_officials) %>%
  head(200)

str(d_accept$sr_12a_actions_contacted_officials_factor)

# Build ordinal logistic regression model
ord_reg_model <- polr(d_accept$sr_12a_actions_contacted_officials_factor ~ 
                        descdynamicnorms_comp + 
                        sr_19a_contacting_officials__parents + desccontactnorms_fam_comp + 
                        desccontactnorms_nf_comp + sr_20a_rolemodels_parents + 
                        descrolemodelnorms_fam_comp + descrolemodelnorms_nf_comp + 
                        sr_22a_expect_contact_parents + injunctcontactnorms_fam_comp + 
                        injunctcontactnorms_nf_comp + injunctmotivation_fam_comp + 
                        injunctmotivation_nf_comp + cimbenefits_comp + 
                        cimperceivedrisk_comp + sr_7_believe_about_climate_change + 
                        sr_11_harm_future_generations + sr_21a_effective_actions_contacting_officials + 
                        efficacy_effectiveness_comp + efficacy_fedstatebusiness_competresp_comp + 
                        efficacy_ngo_competresp_comp + behatt_admirablegood_comp + 
                        behatt_usefulpleasantsensible_comp + behatt_coolexcitingeasy_comp + 
                        sr_30_easy_to_call + sr_31_able_to_call + sr_41a_right_to_modify + 
                        sr_41b_laws_of_nature + sr_41c_ingenuity + sr_41d_impotent + 
                        sr_41e_govt_do_more + sr_41f_equity + age + gender_male + 
                        gender_other + gender_prefernottosay + 
                        sr_56_marital_status_marriedpartner + sr_56_marital_status_divorcedseparated + 
                        sr_56_marital_status_widowed + sr_57i_dependents + sr_57j_adultchildren + 
                        sr_61_education_highschooldegree + sr_61_education_somecollege + 
                        sr_61_education_associatedegree + sr_61_education_bachelordegree + 
                        sr_61_education_gradorprofdegree + sr_71_employment_status_workparttime + 
                        sr_71_employment_status_homemaker + sr_71_employment_status_retired + 
                        sr_71_employment_status_student + sr_71_employment_status_unemployed + 
                        sr_72_income_25to49k + sr_72_income_50to74k + sr_72_income_75to99k + 
                        sr_72_income_100to149k + sr_72_income_150to199k + sr_72_income_200to249k + 
                        sr_72_income_over250k + sr_72_income_prefernottoanswer + race_white_dumvar + 
                        sr_78_political_affiliation_Rep + sr_78_political_affiliation_Ind + 
                        sr_78_political_affiliation_Green + sr_78_political_affiliation_Libertarian + 
                        sr_78_political_affiliation_NoParty + sr_79_political_leaning_SomeLib + 
                        sr_79_political_leaning_Moderate + sr_79_political_leaning_SomeConservative + 
                        sr_79_political_leaning_VeryConservative , data = d_accept, Hess = T)

summary(ord_reg_model)

# Analyze p-values, combine back into summary table
ctable <- coef(summary(ord_reg_model))
p <- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE) * 2
ctable <- cbind(ctable, "p value" = p)
print(ctable)
```

```{r, eval=F, include=F}
# Add CIs for variables
(ci <- confint(ord_reg_model)) # default method gives profiled CIs
confint.default(ord_reg_model) # CIs assuming normality
exp(coef(ord_reg_model))
exp(cbind(OR = coef(ord_reg_model), ci))
```

